---
title: "National Acute Hospital Review"
subtitle: "Emergency Department"
date: "March 2020"
output:
  powerpoint_presentation:
    reference_doc: myStyle.pptx
---

## Contents

```{r setup, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
library(formattable)
library(dplyr)
library(tidyr)
library(plotly)
library(reshape2)
library(extrafont)
library(scales)
library(gtable)
library(grid)

grid_line = element_line(size = 2, color = "grey50")

knitr::opts_chunk$set(warning = FALSE, error = FALSE, message = FALSE, echo = FALSE, fig.height = 50, fig.width = 90, eval=TRUE)

read.csv(file = "~/discharge_codes.csv", stringsAsFactors = FALSE) %>%  subset(admit_status == "Admitted") %>%  pull(discharge_destination) -> admDests

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "blue") %>% pull(code) -> blue

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "red") %>% pull(code) -> red

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "green") %>% pull(code) -> green

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "orange") %>% pull(code) -> orange

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "lightblue") %>% pull(code) -> lightblue

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% 
  
  subset(color == "yellow") %>% pull(code) -> yellow

read.csv(file = "~/MyColors.csv", stringsAsFactors = FALSE) %>% subset(color == "lightbluegrey") %>% pull(code) -> lightbluegrey

x = element_blank()
f1 = element_text(family = "Trebuchet MS", color = "grey31", size = 100)
rotated_f1 = element_text(family = "Trebuchet MS", color = "grey31", size = 100, angle = 90)
title_style = element_text(family = "Trebuchet MS", color = "grey31", size = 110, vjust = 1, face = "bold")
subtitle_style = element_text(family = "Trebuchet MS", color = "grey31", size = 100, face = "italic")
txt_sz = 30
line_sz = 5
pnt_sz = 10
legendFixFill = guides(fill = guide_legend(override.aes = list(size = 30)))
legendFixColor = guides(color = guide_legend(override.aes = list(size = 30)))
source(file = "~/jltable.R")
```

```{r toc, eval=FALSE}
data.frame(section = c("<br>Executive Summary</br>", "<br>ED Attendances</br>", "<br>ED Admissions</br>", "<br>Quadrant Performance</br>", "<br>Patient Experience Time</br>", "<br>Trolleys</br>"),
  
           slidenumber = c("<br>3</br>", "<br>4</br>", "<br>15</br>", "<br>25</br>", "<br>29</br>", "<br>38</br>")
) -> toc

names(toc) = c("<b>Section</b>", "<b>Slide No.</b>")

#toc %>% jltable(fileName = "toc.png")
  
toc %>%  
  
  plot_ly() %>%

  add_table(
  rownames = FALSE,
  header = list(
    align = list("left", "right"),
    line = list(width = 0),
    fill = list(color = lightbluegrey)
  ),
  cells = list(
    align = list("left", "right"),
    line = list(width = 0)
  )
) %>%

  layout(
  font = list(
    family = "Trebuchet MS",
    size = 150,
    colour = "grey31"
  )
)
```

```{r toc1}
data.frame(section = c("Executive Summary", "ED Attendances", "ED Admissions", "Quadrant Performance", "Patient Experience Time", "Trolleys"),
           
           slidenumber = c("3", "4", "15", "25", "29", "38")
) %>%
  
  plot_ly() %>% 
    
    add_table(
      rownames = FALSE,
      header = list(
        values = c("Section", "Slide No."),
        height = 60,
        align = list("left", "right"),
        line = list(width = 0),
        fill = list(color = "skyblue")
      ),
      cells = list(
        height = 50,
        align = list("left", "right"),
        line = list(width = 0)
      )
    ) %>% 
    
    layout(
      font = list(
        family = "Trebuchet MS",
        size = 25,
        colour = "grey31"
      ),
      autosize = FALSE,
      width = 1300,
      height = 975,
      margin = list(t = 5, b = 5, r = 5, l = 5)
    ) %>% 
    
    export(file = "toc.png")
```

## Executive Summary

```{r importEDData, eval=TRUE}
source(file = "~/standard_format.R")

edData = data.frame(
  V1 = as.integer(), 
  V2 = as.character(), 
  V3 = as.character(), 
  V4 = as.integer(), 
  V5 = as.character(), 
  V6 = as.character(), 
  V7 = as.character(), 
  V8 = as.character()
)

acuteIDs = read.csv(
  file = "~/provider_codes.csv",
  stringsAsFactors = FALSE
) %>% 
  subset(
    acuteED == 1
    & complete.cases(biu_hospital_id)
  ) %>% 
  arrange(biu_hospital_id) %>%
  pull(biu_hospital_id)

for(f in c(list.files(path = "C:/Users/jack.lyons/Downloads/PET_Data_01-MMM-YYYY_to_DD-MMM-YYYY/", full.names = TRUE, pattern = "2020"), list.files(path = "C:/Users/jack.lyons/Downloads/PET_Data_01-MMM-YYYY_to_DD-MMM-YYYY/", full.names = TRUE, pattern = "2019"))){

  edData = rbind(edData, read.csv(file = f, stringsAsFactors = FALSE, header = FALSE) %>% subset(V1 %in% acuteIDs) %>% mutate(V3 = standard_format(V3), V7 = standard_format(V7)))
  
}

edData = edData %>% distinct() %>% select(V1,V3,V4,V7,V8) %>% rename(biu_hospital_id = V1, reg = V3, age = V4, depart = V7, destination = V8)
```

```{r loadData}
if(("edData" %in% ls()) == FALSE){
  load("~/edData.RData")
}
```

```{r summary, eval=FALSE}
edData %>% subset(
  reg == max(reg)
) %>% pull(reg) %>% format("%m") %>% as.integer() -> M

edData %>% subset(
  reg == max(reg)
) %>% pull(reg) %>% format("%Y") %>% as.integer() -> Y

edData %>% subset(
  as.integer(
    format(
      reg,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      reg,
      "%m"
    )
  ) == M
) %>% nrow() -> monthattends

edData %>% subset(
  as.integer(
    format(
      reg,
      "%Y"
    )
  ) == Y-1
  & as.integer(
    format(
      reg,
      "%m"
    )
  ) == M
) %>% nrow() -> monthattendslastyear

if(monthattends >= monthattendslastyear){
  paste0(
    "+",
    round(
      100*(monthattends - monthattendslastyear)/monthattendslastyear,
      1
    ),
    "% compared to ",
    format(
      as.Date(
        paste(
          Y-1,
          M,
          1,
          sep = "-"
        )
      ),
      "%B %Y"
    )
  ) -> monthattendscomment
} else {
  paste0(
    round(
      100*(monthattends - monthattendslastyear)/monthattendslastyear,
      1
    ),
    "% compared to ",
    format(
      as.Date(
        paste(
          Y-1,
          M,
          1,
          sep = "-"
        )
      ),
      "%B %Y"
    )
  ) -> monthattendscomment
}

edData %>% subset(
  as.integer(
    format(
      reg,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      reg,
      "%m"
    )
  ) <= M
) %>% nrow() -> ytdattends

edData %>% subset(
  as.integer(
    format(
      reg,
      "%Y"
    )
  ) == Y-1
  & as.integer(
    format(
      reg,
      "%m"
    )
  ) <= M
) %>% nrow() -> ytdattendslastyear

paste0(
  round(
    100*(ytdattends - ytdattendslastyear)/ytdattendslastyear,
    1
  ),
  "% YTD"
) -> ytdattendscomment

if(ytdattends >= ytdattendslastyear){
  ytdattendscomment = paste0(
    "+", 
    ytdattendscomment
  )
}

monthattendsvalue = format(
  monthattends, 
  big.mark = ","
)

ytdattendsvalue = format(
  ytdattends,
  big.mark = ","
)

edData %>% subset(
  as.integer(
    format(
      depart,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      depart,
      "%m"
    )
  ) == M
) %>% mutate(
  pet = as.numeric(
    difftime(
      depart,
      reg,
      units = "hours"
    )
  ),
  pet6 = ifelse(
    pet < 6,
    100,
    0
  )
) %>% pull(pet6) %>% mean() %>% round(1) %>% paste0("%") -> pet6value

if(M == 1){
  edData %>% subset(
    as.integer(
      format(
        depart,
        "%Y"
      )
    ) == Y-1
    & as.integer(
      format(
        depart,
        "%m"
      )
    ) == 12
  ) %>% mutate(
    pet = as.numeric(
      difftime(
        depart,
        reg,
        units = "hours"
      )
    ),
    pet6 = ifelse(
      pet < 6,
      100,
      0
    )
  ) %>% pull(pet6) %>% mean() %>% round(1) %>% paste0("%") -> pet6valuelastmonth
} else {
  edData %>% subset(
    as.integer(
      format(
        depart,
        "%Y"
      )
    ) == Y
    & as.integer(
      format(
        depart,
        "%m"
      )
    ) == M-1
  ) %>% mutate(
    pet = as.numeric(
      difftime(
        depart,
        reg,
        units = "hours"
      )
    ),
    pet6 = ifelse(
      pet < 6,
      100,
      0
    )
  ) %>% pull(pet6) %>% mean() %>% round(1) %>% paste0("%") -> pet6valuelastmonth
}

pet6valuelastmonth = paste0(
  "Prior Month: ",
  pet6valuelastmonth
)

edData %>% subset(
  as.integer(
    format(
      depart,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      depart,
      "%m"
    )
  ) == M
) %>% mutate(
  pet = as.numeric(
    difftime(
      depart,
      reg,
      units = "hours"
    )
  ),
  pet9 = ifelse(
    pet < 9,
    100,
    0
  )
) %>% pull(pet9) %>% mean() %>% round(1) %>% paste0("%") -> pet9value

if(M == 1){
  edData %>% subset(
    as.integer(
      format(
        depart,
        "%Y"
      )
    ) == Y-1
    & as.integer(
      format(
        depart,
        "%m"
      )
    ) == 12
  ) %>% mutate(
    pet = as.numeric(
      difftime(
        depart,
        reg,
        units = "hours"
      )
    ),
    pet9 = ifelse(
      pet < 9,
      100,
      0
    )
  ) %>% pull(pet9) %>% mean() %>% round(1) %>% paste0("%")  -> pet9valuelastmonth
} else {
  edData %>% subset(
    as.integer(
      format(
        depart,
        "%Y"
      )
    ) == Y
    & as.integer(
      format(
        depart,
        "%m"
      )
    ) == M-1
  ) %>% mutate(
    pet = as.numeric(
      difftime(
        depart,
        reg,
        units = "hours"
      )
    ),
    pet9 = ifelse(
      pet < 9,
      100,
      0
    )
  ) %>% pull(pet9) %>% mean() %>% round(1) %>% paste0("%") -> pet9valuelastmonth
}

pet9valuelastmonth = paste0(
  "Prior Month: ",
  pet9valuelastmonth
)

edData %>% subset(
  as.integer(
    format(
      depart,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      depart,
      "%m"
    )
  ) == M
) %>% mutate(
  pet = as.numeric(
    difftime(
      depart,
      reg,
      units = "hours"
    )
  ),
  pet24 = ifelse(
    pet >= 24,
    1,
    0
  )
) %>% pull(pet24) %>% sum() %>% format(big.mark = ",") -> pet24value

edData %>% subset(
  as.integer(
    format(
      depart,
      "%Y"
    )
  ) == Y
  & as.integer(
    format(
      depart,
      "%m"
    )
  ) == M
) %>% mutate(
  pet = as.numeric(
    difftime(
      depart,
      reg,
      units = "hours"
    )
  ),
  petlt24 = ifelse(
    pet < 24,
    100,
    0
  )
) %>% pull(petlt24) %>% mean() %>% round(1) %>% paste0("% of ED departures < 24 hours from registration") -> pet24comment

read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>% mutate(
  date = as.Date.character(
    Target.Date,
    "%d/%m/%Y"
  ),
  year = as.integer(
    format(
      date,
      "%Y"
    )
  ),
  month = as.integer(
    format(
      date,
      "%m"
    )
  )
) %>% subset(
  year == Y
  & month == M
  & !(Hospital.Code %in% c(940, 941, 992))
) %>% pull(Total.8am) %>% sum() -> monthtrolleys

monthtrolleysvalue = format(
  monthtrolleys,
  big.mark = ","
)

read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>% mutate(
  date = as.Date.character(
    Target.Date,
    "%d/%m/%Y"
  ),
  year = as.integer(
    format(
      date,
      "%Y"
    )
  ),
  month = as.integer(
    format(
      date,
      "%m"
    )
  )
) %>% subset(
  year == Y
  & month <= M
  & !(Hospital.Code %in% c(940, 941, 992))
) %>% pull(Total.8am) %>% sum() -> ytdtrolleys

ytdtrolleysvalue = format(
  ytdtrolleys,
  big.mark = ","
)

read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>% mutate(
  date = as.Date.character(
    Target.Date,
    "%d/%m/%Y"
  ),
  year = as.integer(
    format(
      date,
      "%Y"
    )
  ),
  month = as.integer(
    format(
      date,
      "%m"
    )
  )
) %>% subset(
  year == Y-1
  & month == M
  & !(Hospital.Code %in% c(940, 941, 992))
) %>% pull(Total.8am) %>% sum() -> monthtrolleyslastyear

(100*(monthtrolleys - monthtrolleyslastyear)/monthtrolleyslastyear) %>% round(1) %>% paste0(
  "% compared to ",
  format(
    as.Date(
      paste(
        Y-1,
        M,
        1,
        sep = "-"
      )
    ),
    "%B %Y"
  )
) -> monthtrolleyscomment

if(monthtrolleys >= monthtrolleyslastyear){
  paste0(
    "+",
    monthtrolleyscomment
  ) -> monthtrolleyscomment
}

read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>% subset(
  as.integer(
    format(
      as.Date.character(
        Target.Date,
        "%d/%m/%Y"
      ),
      "%Y"
    )
  ) == Y-1
  & as.integer(
    format(
      as.Date.character(
        Target.Date,
        "%d/%m/%Y"
      ),
      "%m"
    )
  ) <= M
  & !(Hospital.Code %in% c(940, 941, 992))
) %>% pull(Total.8am) %>% sum() -> ytdtrolleyslastyear

(100*(ytdtrolleys - ytdtrolleyslastyear)/ytdtrolleyslastyear) %>% round(1) %>% paste0(
  "% YTD"
) -> ytdtrolleyscomment

if(ytdtrolleys >= ytdtrolleyslastyear){
  ytdtrolleyscomment = paste0(
    "+",
    ytdtrolleyscomment
  )
}

data.frame(
  KPI = c(
    "Month Attendances", 
    "YTD Attendances",
    "PET < 6 Hours",
    "PET < 9 Hours",
    "PET >= 24 Hours",
    "Trolleys (8:00 am)",
    "YTD Trolleys (8:00 am)"
  ),
  Values = c(
    monthattendsvalue,
    ytdattendsvalue,
    pet6value,
    pet9value,
    pet24value,
    monthtrolleysvalue,
    ytdtrolleysvalue
  ),
  Comment = c(
    monthattendscomment,
    ytdattendscomment,
    pet6valuelastmonth,
    pet9valuelastmonth,
    pet24comment,
    monthtrolleyscomment,
    ytdtrolleyscomment
  )
) %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(1, 1, 2),
  header = list(
    height = 40,
    align = c(
      "left",
      "left",
      "left"
    ),
    line = list(
      width = 0
    ),
    fill = list(
      color = "skyblue"
    )
  ),
  cells = list(
    height = 40,
    align = c(
      "left",
      "left",
      "left"
    ),
    line = list(
      width = 0
    )
  )
) %>% layout(
  font = list(
    family = "Trebuchet MS",
    size = 25,
    color = "grey31"
  ),
  margin = list(t = 5, b = 5, l = 5, r = 5),
  autosize = FALSE,
  width = 1300,
  height = 975
) %>% export(
  file = "summary.png"
)
```

# ED Attendances

## ED Attendances Trend (Bar)

```{r edAttendsBar}
edData %>% 
  mutate(regmonthnumber = as.integer(format(reg, "%m")), 
         regyear = as.integer(format(reg, "%Y")), 
         regmonth = format(reg, "%B"), 
         count = 1) %>% 
  group_by(regyear, regmonthnumber) %>% 
  mutate(count = sum(count)) %>%
  ungroup() %>%
  select(regmonthnumber, regmonth, regyear, count) %>% 
  distinct() %>% mutate(maxyear = max(regyear), regyear = ifelse(regyear==max(regyear), "Y1", "Y0")) %>% spread(regyear, count) %>% mutate(Y1 = ifelse(is.na(Y1), 0, Y1)) %>% melt(c("regmonth", "regmonthnumber", "maxyear")) %>% rename(count = value, regyear=variable) %>% mutate(regyear = ifelse(regyear == "Y1", maxyear, maxyear-1)) -> D

D %>% ggplot(aes(x = reorder(regmonth, regmonthnumber), y = count, fill = factor(regyear))) + 
  
  geom_bar(stat = "identity", position = "dodge") +
  
  geom_text(color = "white", size = txt_sz, aes(x = regmonth, y = count, label = ifelse(count ==0, "", format(count, big.mark = ",")), family = "Trebuchet MS"), 
            
            angle = 90,
            
            vjust = ifelse(D$regyear == max(D$regyear), 2, -1),
            
            hjust = 1
            
            ) +
  
  labs(title = "ED Attendances") + 
  
  scale_fill_manual(values = c(red, blue)) +
  
  scale_y_continuous(limits = c(0, 1.1*max(D$count))) +
  
  theme(panel.background = x, legend.title = x, text = f1, axis.line = x, legend.position = "top", axis.title = x, axis.text.x = rotated_f1, axis.text.y = x, plot.title = title_style) + 
  
  guides(fill = guide_legend(override.aes = list(size = 30)))
```

## ED Attendances Age Profile Trend

```{r agetrend}
edData %>% mutate(
  agegroup = ifelse(
    is.na(age) | age < 0 | age >= 110,
    "Unknown",
    ifelse(
      age < 16,
      "Paediatrics: 0-15",
      ifelse(
        age >= 16 & age < 75,
        "Adults: 16-74",
        "Adults: 75+"
      )
    )
  ),
  count = 1,
  month = as.Date(
    format(
      reg,
      "%Y-%m-01"
    )
  )
) %>% group_by(
  month,
  agegroup
) %>% mutate(
  count = sum(count)
) %>% ungroup() %>% select(
  month, 
  agegroup,
  count
) %>% distinct() %>% arrange(
  month
) -> D

D %>% ggplot(aes(x = month, y = count)) + 
  
  geom_line(aes(color = agegroup), size = line_sz) + geom_point(aes(color = agegroup), key_glyph = "rect", size = pnt_sz) +
  
  geom_text(color = "grey31", size = txt_sz, aes(x = month, y = count, label = format(count, big.mark = ","), family = "Trebuchet MS", vjust = "top")) +
  
  labs(title = "ED Attendances") + 
  
  scale_color_manual(values = c(red, green, blue, orange)) +
  
  scale_x_date(breaks = D$month, labels = format(D$month, "%B %Y")) +
  
  theme(panel.background = x, legend.title = x, text = f1, axis.line = element_line(color = "grey31", size = 2), legend.position = "top", legend.key = x, axis.title = x, axis.text.x = rotated_f1, panel.grid.major = grid_line) + legendFixColor
```

## ED Attendances Age Profile Trend (% of Total)

```{r agepctrend}
edData %>% mutate(
  agegroup = ifelse(
    is.na(age) | age < 0 | age >= 110,
    "Unknown",
    ifelse(
      age < 16,
      "Paediatrics: 0-15",
      ifelse(
        age >= 16 & age < 75,
        "Adults: 16-74",
        "Adults: 75+"
      )
    )
  ),
  count = 1,
  month = as.Date(
    format(
      reg,
      "%Y-%m-01"
    )
  )
) %>% group_by(
  month
) %>% mutate(monthcount = sum(count)) %>% group_by(
  month,
  agegroup
) %>% mutate(
  count = sum(count)
) %>% ungroup() %>% select(
  month, 
  agegroup,
  count,
  monthcount
) %>% distinct() %>% arrange(
  month
) %>% mutate(
  value = count/monthcount,
  label = paste0(
    round(
      100*value,
      1
    ),
    "%"
  )
) -> D

D %>% ggplot(aes(x = month, y = value)) + 
  
  geom_line(aes(color = agegroup), size = line_sz) + geom_point(aes(color = agegroup), size = pnt_sz, key_glyph = "rect") +
  
  geom_text(color = "grey31", size = txt_sz, aes(x = month, y = value, label = label, family = "Trebuchet MS"), vjust = "top") +
  
  labs(title = "Portion of Total ED Attendances") + 
  
  scale_y_continuous(breaks = seq(0, 0.8, by = 0.1), labels = paste0(round(100*seq(0, 0.8, by = 0.1)), "%")) +
  
  scale_x_date(breaks = D$month, labels = format(D$month, "%B %Y")) +
  
  scale_color_manual(values = c(red, green, blue, orange)) +
  
  theme(panel.background = x, legend.title = x, text = f1, axis.line = element_line(color = "grey31", size = 1), legend.position = "top", legend.key = x, axis.title = x, axis.text.x = rotated_f1, panel.grid.major = grid_line) + legendFixColor
```

```{r edAttendsScatter, eval = FALSE}
edAttendsLastYear = edData %>% 
  mutate(monthNumber = as.integer(format(reg, "%m")), 
         year = as.integer(format(reg, "%Y")), 
         month = format(as.Date(paste(year, monthNumber, 1, sep = "-")), "%B"), 
         count = 1) %>% 
  subset(year == max(year)-1) %>%
  group_by(monthNumber) %>% 
  mutate(lastYearsCount = sum(count)) %>% 
  select(monthNumber, month, year, lastYearsCount) %>% 
  distinct()

edAttendsPresentYear = edData %>% 
  mutate(monthNumber = as.integer(format(reg, "%m")), 
         year = as.integer(format(reg, "%Y")), 
         month = format(as.Date(paste(year, monthNumber, 1, sep = "-")), "%B"), 
         count = 1) %>% 
  subset(year == max(year)) %>%
  group_by(monthNumber) %>% 
  mutate(thisYearsCount = sum(count)) %>% 
  select(monthNumber, month, year, thisYearsCount) %>% 
  distinct()

edAttendsByMonth = merge(x = edAttendsLastYear %>% select(monthNumber, month, lastYearsCount), 
      y = edAttendsPresentYear %>% select(monthNumber, month, thisYearsCount),
      by = c("monthNumber", "month"),
      all = TRUE) %>% 
  mutate(presentYear = max(edAttendsPresentYear$year))

future = edAttendsByMonth %>% subset(is.na(thisYearsCount)) %>% select(monthNumber, presentYear) %>% mutate(month = format(as.Date(paste(presentYear, monthNumber, 1, sep = "-")), "%B"))
pd = lm(lastYearsCount~monthNumber, data = edAttendsByMonth) %>% predict(future, interval = "predict") %>% data.frame() %>% cbind(future) %>% merge(y = edAttendsByMonth, by = c("monthNumber", "month", "presentYear"), all = TRUE) %>% arrange(monthNumber)

pd %>% plot_ly(x = ~monthNumber) %>% 
  add_markers(y = ~lastYearsCount, name = "2019 Data", size = 3) %>%
  add_markers(y = ~thisYearsCount, name = "2020 Data", size = 3) %>%
  add_lines(y = ~upr, name = "95% Prediction Interval", line = list(dash = "dash", color = "lightblue")) %>%
  add_lines(y = ~lwr, name = "Lower Prediction", showlegend = FALSE, line = list(dash = "dash", color = "lightblue")) %>%
  layout(xaxis = list(tickvals = ~monthNumber, ticktext = ~month, title = "", tickangle = 90), 
         yaxis = list(title = "Attendances"), 
         font = list(family = "Trebuchet MS", size = 18, color = "grey31"),
         legend = list(orientation = "h", x = 0, y = 1.1),
         autosize = FALSE, width = 1300, height = 975,
         margin = list(r = 5, l = 5, b = 5, t = 5)) %>%
  export(file = "edAttendsScatter.png")
```

## ED Attendances Age Profile

```{r edAttendsAgePie, eval = FALSE}
edData %>% mutate(month = as.Date(format(reg, "%Y-%m-01"))) %>% 
  subset(month == max(month)) %>% 
  mutate(ageGroup = ifelse(is.na(age) | age < 0 | age >= 110, "Unknown", 
                           ifelse(age < 16, "Paediatrics: 0-15", 
                                  ifelse(age >= 16 & age < 75, "Adults: 16-74", 
                                         "Adults: 75+"))),
         count = 1) %>%
  group_by(ageGroup) %>%
  mutate(count = sum(count)) %>%
  select(ageGroup, count) %>%
  distinct() %>%
  
  arrange(ageGroup) %>%
  
  plot_ly() %>%
  add_pie(values = ~count, labels = ~ageGroup, textinfo = "label+value+percent", showlegend = FALSE, marker = list(colors = c(red, green, blue, orange))) %>%
  layout(font = list(family = "Trebuchet MS", size = 100, color = "grey31"),
         #autosize = FALSE, width = 1300, height = 975,
         margin = list(r = 5, l = 5, t = 5, b = 5))
```

```{r edAttendsAgePie2}
edData %>% mutate(month = as.Date(format(reg, "%Y-%m-01"))) %>% 
  subset(month == max(month)) %>% 
  mutate(ageGroup = ifelse(is.na(age) | age < 0 | age >= 110, "Unknown", 
                           ifelse(age < 16, "Paediatrics: 0-15", 
                                  ifelse(age >= 16 & age < 75, "Adults: 16-74", 
                                         "Adults: 75+"))),
         count = 1) %>%
  group_by(ageGroup) %>%
  mutate(count = sum(count)) %>%
  
  ungroup() %>%
  
  distinct(month, ageGroup, count) %>%
  
  arrange(desc(ageGroup)) %>%
  
  mutate(portion = 100*count/sum(count), ypos = ifelse(ageGroup == "Unknown", 90, cumsum(portion) - 0.5*portion), lbl = paste0(round(portion, 1), "%")) -> D

D %>% pull(month) %>% unique() %>% format("%B %Y") -> sbttl

D %>% ggplot(aes(x = "", fill = ageGroup)) + geom_bar(aes(y = portion), stat = "identity") + coord_polar(theta = "y", direction = -1, start = 0) + scale_fill_manual(values = c(red, green, blue, orange)) + theme(panel.background = x, legend.title = x, legend.text = f1, legend.position = "bottom", legend.direction = "horizontal", axis.title = x, axis.ticks = x, axis.text = x) + geom_text(color = "grey31", aes(y = ypos, label = paste(ageGroup, format(count, big.mark = ","), lbl, sep = "\n")), family = "Trebuchet MS", size = txt_sz*1.2) + legendFixFill + labs(title = "ED Attendances Age Profile", subtitle = sbttl) + theme(plot.title = title_style, plot.subtitle = subtitle_style)
```

## ED Attendances Month & YTD

```{r edTable, eval=FALSE}
edAttendsByHosp = edData %>% mutate(month = as.integer(format(reg, "%m")), 
                                    year = as.integer(format(reg, "%Y")),
                                    lastYearsCount = ifelse(year == max(year)-1, 1, 0),
                                    thisYearsCount = ifelse(year == max(year), 1, 0)) %>% 
  subset(year >= max(year)-1) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAttendsTable.png")
```

## ED Attendances (Ages: 0-15) Month & YTD

```{r edTable015, eval=FALSE}
edAttendsByHosp = edData %>% mutate(month = as.integer(format(reg, "%m")), 
                                    year = as.integer(format(reg, "%Y")),
                                    lastYearsCount = ifelse(year == max(year)-1, 1, 0),
                                    thisYearsCount = ifelse(year == max(year), 1, 0)) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 0
    & age < 16
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAttendsTable015.png")
```

## ED Attendances (Ages: 16-74) Month & YTD

```{r edTable1674, eval=FALSE}
edAttendsByHosp = edData %>% mutate(month = as.integer(format(reg, "%m")), 
                                    year = as.integer(format(reg, "%Y")),
                                    lastYearsCount = ifelse(year == max(year)-1, 1, 0),
                                    thisYearsCount = ifelse(year == max(year), 1, 0)) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 16
    & age < 75
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAttendsTable1674.png")
```

## ED Attendances (Ages: 75+) Month & YTD

```{r edTable75, eval=FALSE}
edAttendsByHosp = edData %>% mutate(month = as.integer(format(reg, "%m")), 
                                    year = as.integer(format(reg, "%Y")),
                                    lastYearsCount = ifelse(year == max(year)-1, 1, 0),
                                    thisYearsCount = ifelse(year == max(year), 1, 0)) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 75
    & age < 110
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAttendsTable75.png")

```

## ED Attendances (Ages: Unknown) Month & YTD

```{r edTableUnknown, eval=FALSE}
edAttendsByHosp = edData %>% mutate(month = as.integer(format(reg, "%m")), 
                                    year = as.integer(format(reg, "%Y")),
                                    lastYearsCount = ifelse(year == max(year)-1, 1, 0),
                                    thisYearsCount = ifelse(year == max(year), 1, 0)) %>% 
  subset(
    year >= max(year)-1
    & (is.na(age)
    | age >= 110
    | age < 0)
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAttendsTableUnknown.png")
```

## ED Departures By Destination

```{r destinationTable}
edData %>% 
  mutate(
    count = 1,
    regmonth = as.Date(
      format(
        reg, 
        "%Y-%m-01"
      )
    ),
    departmonth = as.Date(
      format(
        depart,
        "%Y-%m-01"
      )
    )
  ) %>%
  subset(departmonth == max(regmonth)) %>%
  group_by(destination) %>%
  mutate(count = sum(count)) %>%
  ungroup() %>%
  select(departmonth, destination, count) %>%
  distinct() %>%
  mutate(portion = count/sum(count)) %>%
  arrange(-portion) -> d

d %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

d1 = rbind(
  d %>% select(destination, count, portion),
  data.frame(
    destination = "<b>Total ED Departures</b>",
    count = sum(d$count),
    portion = 1
  )
) %>%
  mutate(
    count = ifelse(destination == "<b>Total ED Departures</b>", paste0("<b>", format(count, big.mark = ","), "</b>"), format(count, big.mark = ",")),
    portion = ifelse(destination == "<b>Total ED Departures</b>", paste0("<b>100%</b>"), paste0(round(100*portion, 1), "%")), count = gsub(" ", "", count))

d1 %>% plot_ly() %>%
  add_table(
    rownames = FALSE,
    columnwidth = c(2,1,1),
    header = list(
      height = 30,
      values = c(
        paste0("<b>ED Departures</b><br><i>", sbttl, "</i><br><br><b>Destination</b>"),
        "<br><br><br><br><b>Total</b>",
        "<br><br><br><br><b>% of Total</b>"
      ),
      line = list(width = 0),
      align = rep("left", 3)
    ),
    cells = list(
      height = 30,
      align = rep("left", 3),
      line = list(width = 0),
      fill = list(
        color = list(
          rep(
            c(
              rep("white", nrow(d1)-1),
              "white"
            ),
            3
          )
        )
      )
    )
  ) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 25,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, l = 5, r = 5)
  ) %>%
  export(file = "destinationTable.png")
```


# ED Admissions

## ED Admissions Trend (Bar)

```{r admtrend}
edData %>% mutate(
  regmonth = as.integer(format(reg, "%m")), 
  regyear = as.integer(format(reg, "%Y")), 
  departyear = as.integer(format(depart, "%Y")),
  departmonth = format(depart, "%b"),
  departmonthnumber = as.integer(format(depart, "%m")),
  count = 1
) %>% subset(
  destination %in% admDests
  & complete.cases(departyear)
  & as.Date(depart) <= max(as.Date(reg))
) %>% subset(departyear >= max(departyear)-1) %>% group_by(
  departyear, 
  departmonth,
  departmonthnumber
) %>% mutate(
  count = sum(count)
) %>% ungroup() %>% select(
  departyear,
  departmonth,
  departmonthnumber,
  count
) %>% 
  
  distinct() %>%

  mutate(maxyear = max(departyear), departyear = ifelse(departyear==max(departyear), "Y1", "Y0")) %>% 
  
  spread(departyear, count) %>% 
  
  mutate(Y1 = ifelse(is.na(Y1), 0, Y1)) %>% 
  
  melt(c("departmonth", "departmonthnumber", "maxyear")) %>% 
  
  rename(count = value, departyear=variable) %>% 
  
  mutate(departyear = ifelse(departyear == "Y1", maxyear, maxyear-1)) -> D



D %>% ggplot(aes(x = reorder(departmonth, departmonthnumber), y = count, fill = factor(departyear))) + 
  
  geom_bar(stat = "identity", position = "dodge") +
  
  geom_text(color = "white", size = txt_sz, aes(x = departmonth, y = count, label = ifelse(count ==0, "", format(count, big.mark = ",")), family = "Trebuchet MS"), 
            
            angle = 90,
            
            vjust = ifelse(D$departyear == max(D$departyear), 2, -1),
            
            hjust = 1
            
            ) +
  
  labs(title = "ED Attendances") + 
  
  scale_fill_manual(values = c(red, blue)) +
  
  scale_y_continuous(limits = c(0, 1.1*max(D$count))) +
  
  theme(panel.background = x, legend.title = x, text = f1, axis.line = x, legend.position = "top", axis.title = x, axis.text.x = rotated_f1, axis.text.y = x, plot.title = title_style) + 
  
  guides(fill = guide_legend(override.aes = list(size = 30)))
```

## ED Admissions Age Profile

```{r edAdmissionsAgePie, eval=FALSE}
edData %>% 
  
  mutate(
    regmonth = as.Date(format(reg, "%Y-%m-01")),
    departmonth = as.Date(format(depart, "%Y-%m-01"))
  ) %>% 
  
  subset(departmonth == max(regmonth) & destination %in% admDests) %>% 
  
  mutate(ageGroup = ifelse(is.na(age) | age < 0 | age >= 110, "Unknown", 
                           ifelse(age < 16, "Paediatrics: 0-15", 
                                  ifelse(age >= 16 & age < 75, "Adults: 16-74", 
                                         "Adults: 75+"))),
         count = 1) %>%
  group_by(ageGroup) %>%
  mutate(count = sum(count)) %>%
  distinct(departmonth, ageGroup, count) %>%
  
  arrange(ageGroup) %>%
  
  plot_ly() %>%
  add_pie(values = ~count, labels = ~ageGroup, textinfo = "label+value+percent", showlegend = FALSE, marker = list(colors = c(red, green, blue, orange))) %>%
  layout(font = list(family = "Trebuchet MS", size = 100, color = "grey31"),
         #autosize = FALSE, width = 1300, height = 975,
         margin = list(r = 5, l = 5, t = 5, b = 5))
```

```{r edAdmissionsAgePie2}
edData %>% 
  mutate(
    regmonth = as.Date(format(reg, "%Y-%m-01")),
    departmonth = as.Date(format(depart, "%Y-%m-01"))
  ) %>% 
  subset(departmonth == max(regmonth) & destination %in% admDests) %>% 
  mutate(ageGroup = ifelse(is.na(age) | age < 0 | age >= 110, "Unknown", 
                           ifelse(age < 16, "Paediatrics: 0-15", 
                                  ifelse(age >= 16 & age < 75, "Adults: 16-74", 
                                         "Adults: 75+"))),
         count = 1) %>%
  group_by(ageGroup) %>%
  mutate(count = sum(count)) %>%
  
  ungroup() %>%
  
  distinct(departmonth, ageGroup, count) %>%
  
  arrange(desc(ageGroup)) %>%
  
  mutate(portion = 100*count/sum(count), ypos = ifelse(ageGroup == "Unknown", 90, cumsum(portion) - 0.5*portion), lbl = paste0(round(portion, 1), "%")) -> D

D %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

D %>% ggplot(aes(x = "", fill = ageGroup)) + geom_bar(aes(y = portion), stat = "identity") + coord_polar(theta = "y", direction = -1, start = 0) + scale_fill_manual(values = c(red, green, blue, orange)) + theme(panel.background = x, legend.title = x, legend.text = f1, legend.position = "bottom", legend.direction = "horizontal", axis.title = x, axis.ticks = x, axis.text = x) + geom_text(color = "grey31", aes(y = ypos, label = paste(ageGroup, format(count, big.mark = ","), lbl, sep = "\n")), family = "Trebuchet MS", size = txt_sz*1.2) + legendFixFill + labs(title = "ED Admissions Age Profile", subtitle = sbttl) + theme(plot.title = title_style, plot.subtitle = subtitle_style)
```

## ED Admissions Month & YTD

```{r edAdmissionsTable, eval = FALSE}
edAttendsByHosp = edData %>% subset(
  as.Date(depart) <= as.Date(reg)
) %>% mutate(
  month = as.integer(format(depart, "%m")), 
  year = as.integer(format(depart, "%Y")),
  lastYearsCount = ifelse(year == max(year)-1, 1, 0),
  thisYearsCount = ifelse(year == max(year), 1, 0)
) %>% 
  subset(
    year >= max(year)-1
    
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAdmissionsTable.png")
```

## ED Admissions (Ages: 0-15) Month & YTD

```{r edAdmissionsTable015, eval = FALSE}
edAttendsByHosp = edData %>% subset(
  as.Date(depart) <= as.Date(reg)
) %>% mutate(
  month = as.integer(format(depart, "%m")), 
  year = as.integer(format(depart, "%Y")),
  lastYearsCount = ifelse(year == max(year)-1, 1, 0),
  thisYearsCount = ifelse(year == max(year), 1, 0)
) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 0
    & age < 16
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAdmissionsTable015.png")

```

## ED Admissions (Ages: 16-74) Month & YTD

```{r edAdmissionsTable1674, eval = FALSE}
edAttendsByHosp = edData %>% subset(
  as.Date(depart) <= as.Date(reg)
) %>% mutate(
  month = as.integer(format(depart, "%m")), 
  year = as.integer(format(depart, "%Y")),
  lastYearsCount = ifelse(year == max(year)-1, 1, 0),
  thisYearsCount = ifelse(year == max(year), 1, 0)
) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 16
    & age < 75
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAdmissionsTable1674.png")

```

## ED Admissions (Ages: 75+) Month & YTD

```{r edAdmissionsTable75, eval = FALSE}
edAttendsByHosp = edData %>% subset(
  as.Date(depart) <= as.Date(reg)
) %>% mutate(
  month = as.integer(format(depart, "%m")), 
  year = as.integer(format(depart, "%Y")),
  lastYearsCount = ifelse(year == max(year)-1, 1, 0),
  thisYearsCount = ifelse(year == max(year), 1, 0)
) %>% 
  subset(
    year >= max(year)-1
    & complete.cases(age)
    & age >= 75
    & age < 110
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAdmissionsTable75.png")

```

## ED Admissions (Ages: Unknown) Month & YTD

```{r edAdmissionsTableUnknown, eval = FALSE}
edAttendsByHosp = edData %>% subset(
  as.Date(depart) <= as.Date(reg)
) %>% mutate(
  month = as.integer(format(depart, "%m")), 
  year = as.integer(format(depart, "%Y")),
  lastYearsCount = ifelse(year == max(year)-1, 1, 0),
  thisYearsCount = ifelse(year == max(year), 1, 0)
) %>% 
  subset(
    year >= max(year)-1
    & (is.na(age)
    | age >= 110
    | age < 0)
  ) %>% 
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>%
          select(biu_hospital_id, hospital_group_long_name, hospital),
        by = "biu_hospital_id", all = FALSE) %>%
  group_by(month, hospital) %>%
  mutate(lastYearsCount = sum(lastYearsCount),
         thisYearsCount = sum(thisYearsCount)) %>%
  ungroup() %>%
  mutate(presentYear = max(year)) %>%
  select(hospital_group_long_name, hospital, month, presentYear, lastYearsCount, thisYearsCount) %>%
  distinct() %>% arrange(hospital_group_long_name, hospital, month) %>%
  group_by(hospital) %>% 
  mutate(ytdLastYearsCount = cumsum(lastYearsCount),
         ytdThisYearsCount = cumsum(thisYearsCount)) %>%
  ungroup() %>% 
  subset(thisYearsCount != 0 & complete.cases(thisYearsCount)) %>% 
  subset(month == max(month)) %>%
  select(presentYear, month, hospital_group_long_name, hospital, lastYearsCount, thisYearsCount, ytdLastYearsCount, ytdThisYearsCount) %>%
  mutate(change = ifelse(complete.cases(lastYearsCount) & lastYearsCount != 0,
                         ifelse(lastYearsCount > thisYearsCount,
                                paste0(round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%"),
                                paste0("+", round(100*(thisYearsCount-lastYearsCount)/lastYearsCount, 1), "%")),
                         ""),
         ytdChange = ifelse(complete.cases(ytdLastYearsCount) & ytdLastYearsCount != 0,
                            ifelse(ytdLastYearsCount > ytdThisYearsCount,
                                   paste0(round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%"),
                                   paste0("+", round(100*(ytdThisYearsCount - ytdLastYearsCount)/ytdLastYearsCount, 1), "%")),
                            "")) %>% 
  subset(complete.cases(hospital)) %>%
  data.frame() %>%
  mutate(gap1 = "", gap2 = "")


MMMM = format(as.Date(paste(max(edAttendsByHosp$presentYear)-1,
                            max(edAttendsByHosp$month),
                            1, sep = "-")), "%B")

YYYY1 = max(edAttendsByHosp$presentYear)
YYYY0 = YYYY1 - 1

totalRow = data.frame(lastYearsCount = sum(edAttendsByHosp$lastYearsCount),
                      thisYearsCount = sum(edAttendsByHosp$thisYearsCount),
                      gap1 = "",
                      ytdLastYearsCount = sum(edAttendsByHosp$ytdLastYearsCount),
                      ytdThisYearsCount = sum(edAttendsByHosp$ytdThisYearsCount),
                      gap2 = "",
                      hospital_group_long_name = "Total",
                      hospital = "")

totalRow$change = ifelse(totalRow$lastYearsCount > totalRow$thisYearsCount,
                         paste0(round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"),
                         paste0("+", round(100*(totalRow$thisYearsCount - totalRow$lastYearsCount)/totalRow$lastYearsCount, 1), "%"))

totalRow$ytdChange = ifelse(totalRow$ytdLastYearsCount > totalRow$ytdThisYearsCount,
                            paste0(round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"),
                            paste0("+", round(100*(totalRow$ytdThisYearsCount - totalRow$ytdLastYearsCount)/totalRow$ytdLastYearsCount, 1), "%"))

rbind(
  edAttendsByHosp %>%
    select(
      hospital_group_long_name,
      hospital,
      thisYearsCount, 
      ytdThisYearsCount,
      gap1,
      lastYearsCount,
      ytdLastYearsCount,
      gap2, 
      change, 
      ytdChange
    ),
  totalRow
) %>% mutate(
  hospital_group_long_name = ifelse(
    duplicated(hospital_group_long_name),
    "",
    hospital_group_long_name
  )
) -> edAttendsByHosp

for(c in c("lastYearsCount", "thisYearsCount", "ytdLastYearsCount", "ytdThisYearsCount")){
  edAttendsByHosp[, c] = format(edAttendsByHosp[, c], big.mark = ",")
}

edAttendsByHosp %>% plot_ly() %>% add_table(
  rownames = FALSE,
  columnwidth = c(4, 2, rep(1, 8)),
  header = list(
    values = c(
      "",
      "", 
      paste(MMMM, YYYY0, sep = "<br>"),
      paste0(MMMM, "<br>", YYYY0, " YTD"),
      "",
      paste(MMMM, YYYY1, sep = "<br>"), 
      paste0(MMMM, "<br>", YYYY1, " YTD"), 
      "", 
      "% Change<br>Month", 
      "% Change<br>YTD"
    ),
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = c(
        "skyblue", "skyblue", "skyblue", "skyblue", 
        "white", 
        "skyblue", "skyblue", 
        "white",  
        "skyblue", "skyblue"
      )
    )
  ),
  cells = list(
    height = 25,
    align = c("left", "left", rep("center", 8)),
    line = list(width = 0),
    fill = list(
      color = list(
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        "white",
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue"),
        c(rep("white", nrow(edAttendsByHosp)-1), "skyblue")
      )
    )
  )
) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>%
  export(file = "edAdmissionsTableUnknown.png")

```

## Admission % by Hospital

```{r admRateByHosp}
edData %>% 
  mutate(
    regmonth = as.Date(format(reg, "%Y-%m-01")),
    departmonth = as.Date(format(depart, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth)) %>%
  mutate(
    departures = 1,
    adm = ifelse(destination %in% admDests, 1, 0),
    nadm = ifelse(!(destination %in% admDests), 1, 0)
  ) %>%
  group_by(biu_hospital_id) %>%
  mutate(
    admcount = sum(adm),
    nadmcount = sum(nadm)
  ) %>%
  
  ungroup() %>% 
  
  distinct(departmonth, biu_hospital_id, admcount, nadmcount) %>%
  
  melt(id.vars = c("biu_hospital_id", "departmonth")) %>%
  
  group_by(biu_hospital_id) %>%
  
  mutate(departures = sum(value)) %>% 
  
  ungroup() %>%
  
  mutate(rate = paste0(round(100*value/departures, 1), "%"), label = paste0(format(value, big.mark = ","), " (", rate, ")")) %>%
  
  #mutate(rate = paste0(round(100*value/departures, 1), "%"), label = ifelse(variable == "admcount", paste0(format(value, big.mark = ","), " (", rate, ")"), format(value, big.mark = ","))) %>%
  
  merge(y = read.csv(file = "~/provider_codes.csv", stringsAsFactors = FALSE) %>% select(biu_hospital_id, hospital), by = "biu_hospital_id", all.x = TRUE) %>%
  
  mutate(variable = ifelse(variable == "admcount", "Admitted", "Not-Admitted"), position = ifelse(variable == "Admitted", departures-value, 0), departmonth = format(departmonth, "%B %Y")) %>%
  
  distinct(departmonth, hospital, variable, value, departures, position, label) -> D

D %>% ggplot(aes(x = reorder(hospital, departures),  fill = variable)) + geom_bar(stat = "identity", aes(y = value)) + coord_flip() + geom_text(color = "grey31", aes(y = position, label = label), hjust = "left", family = "Trebuchet MS", size = txt_sz) + theme(axis.title = x, axis.ticks = x, axis.text = f1, panel.background = x, panel.grid.major.x = grid_line, legend.position = "top", legend.direction = "horizontal", legend.title = x, legend.text = f1, plot.title = title_style, plot.subtitle = subtitle_style) + scale_y_continuous(labels = scales::comma) + scale_fill_manual(values = c(blue, lightblue)) + labs(title = "ED Departures", subtitle = D %>% pull(departmonth) %>% unique()) + legendFixFill
```

## Admissions by Destination

```{r admDestinationTable}
d = edData %>% 
  subset(destination %in% admDests & complete.cases(depart)) %>%
  mutate(
    count = 1,
    regmonth = as.Date(
      format(
        reg, 
        "%Y-%m-01"
      )
    ),
    departmonth = as.Date(
      format(
        depart,
        "%Y-%m-01"
      )
    )
  ) %>%
  subset(departmonth == max(regmonth)) %>%
  group_by(destination) %>%
  mutate(count = sum(count)) %>%
  ungroup() %>%
  select(departmonth, destination, count) %>%
  distinct() %>%
  mutate(portion = count/sum(count)) %>%
  arrange(-portion)

d %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

d1 = rbind(
  d %>% select(destination, count, portion),
  data.frame(
    destination = "<b>Total ED Admissions</b>",
    count = sum(d$count),
    portion = 1
  )
) %>%
  mutate(
    count = format(count, big.mark = ","),
    portion = paste0(
      round(100*portion, 1),
      "%"
    ),
    count = ifelse(destination == "Total ED Admissions", paste0("<b>", count, "</b>"), count),
    portion = ifelse(destination == "Total ED Admissions", "<b>100%</b>", portion),
    count = gsub(" ", "", count)
  )

d1 %>% plot_ly() %>%
  add_table(
    rownames = FALSE,
    columnwidth = c(2,1,1),
    header = list(
      height = 30,
      values = c(
        paste0("<b>ED Admissions</b><br><i>", sbttl, "</i><br><br><b>Destination</b>"),
        "<br><br><br><br><b>Total</b>",
        "<br><br><br><br><b>% of Total</b>"
      ),
      fill = list(color = "white"),
      line = list(width = 0),
      align = rep("left", 3)
    ),
    cells = list(
      height = 30,
      align = rep("left", 3),
      line = list(width = 0),
      fill = list(
        color = list(
          rep(
            c(
              rep("white", nrow(d1)-1),
              "white"
            ),
            3
          )
        )
      )
    )
  ) %>%
    layout(
      font = list(
        family = "Trebuchet MS",
        size = 22,
        color = "grey31"
      ),
      autosize = FALSE,
      width = 1300,
      height = 975,
      margin = list(t = 5, b = 5, l = 5, r = 5)
    ) %>%
    export(file = "admDestinationTable.png")
#d1 %>% jltable(fileName = "tbl2.png", last_row_is_total = TRUE)  
```


# Quadrant Performance

## Note

ED records of patients with an age on registration less than 16 years are excluded from calculation of average PET and departure count.

## Trolleys per 100 Departures Vs Mean PET

```{r quadrant1, eval = FALSE}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(
    complete.cases(depart) 
    & departmonth == max(regmonth)
    & complete.cases(age)
    & age >= 16
  ) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>% select(biu_hospital_id, hospital),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    count = sum(count),
    pet = mean(pet)
  ) %>%
  ungroup() %>%
  select(hospital, count, pet) %>%
  distinct() %>% merge(
    y = read.csv(
      file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
      stringsAsFactors = FALSE
    ) %>% select(Hospital.Code, Target.Date, Total.8am) %>% rename(
      biu_hospital_id = Hospital.Code,
      date = Target.Date,
      total8am = Total.8am
    ) %>% mutate(
      date = as.Date(
        format(
          as.Date.character(
            date,
            "%d/%m/%Y"
          ),
          "%Y-%m-01"
        )
      )
    ) %>% subset(
      date == max(date)
    ) %>% group_by(biu_hospital_id) %>% mutate(
      total8am = sum(total8am)
    ) %>% ungroup() %>% select(
      biu_hospital_id, total8am
    ) %>% distinct() %>% merge(
      y = read.csv(
        file = "~/provider_codes.csv",
        stringsAsFactors = FALSE
      ) %>% select(biu_hospital_id, hospital, hospital_group_long_name),
      by = "biu_hospital_id",
      all.x = TRUE
    ) %>% select(hospital_group_long_name, hospital, total8am),
    by = "hospital",
    all = TRUE
  ) %>% mutate(
    yv = total8am*100/count
  ) %>% subset(
    !(hospital %in% c("Temple Street", "Tallaght Paed", "Crumlin")) 
  ) -> D

D %>% plot_ly() %>% add_markers(
  x = ~pet,
  y = ~yv,
  name = ~hospital_group_long_name,
  marker = list(size = 30)) %>% 
  
  add_lines(
  y = ~median(yv),
  x = ~pet,
  line = list(width = 10, color = green),
  name = ~paste(
    "Median:", 
    round(
      median(yv),
      1
    )
  )
) %>% add_lines(
  x = ~median(pet),
  y = ~yv,
  line = list(width = 10,
    color = red
  ),
  name = ~paste(
    "Median:", 
    round(
      median(pet),
      1
    )
  )
) %>% add_annotations(
  text = ~hospital,
  x = ~pet,
  y = ~yv,
  showarrow = FALSE,
  yanchor = "top"
) %>% layout(
  legend = list(
    orientation = "h",
    x = 0,
    y = 1.1
  ),
  xaxis = list(
    title = "Average PET for ED Departures (Hours)"
  ),
  yaxis = list(
    title = "Trolleys per 100 ED Departures"
  ),
  font = list(
    family = "Trebuchet MS",
    size = 80,
    color = "grey31"
  ),
  margin = list(t = 5, b = 5, r = 5, l = 5))
```

```{r quadrant1_v2}
x = element_blank()

edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(
    complete.cases(depart) 
    & departmonth == max(regmonth)
    & complete.cases(age)
    & age >= 16
  ) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>% select(biu_hospital_id, hospital),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    count = sum(count),
    pet = mean(pet)
  ) %>%
  ungroup() %>%
  select(hospital, count, pet) %>%
  distinct() %>% merge(
    y = read.csv(
      file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
      stringsAsFactors = FALSE
    ) %>% select(Hospital.Code, Target.Date, Total.8am) %>% rename(
      biu_hospital_id = Hospital.Code,
      date = Target.Date,
      total8am = Total.8am
    ) %>% mutate(
      date = as.Date(
        format(
          as.Date.character(
            date,
            "%d/%m/%Y"
          ),
          "%Y-%m-01"
        )
      )
    ) %>% subset(
      date == max(date)
    ) %>% group_by(biu_hospital_id) %>% mutate(
      total8am = sum(total8am)
    ) %>% ungroup() %>% select(
      date, biu_hospital_id, total8am
    ) %>% distinct() %>% merge(
      y = read.csv(
        file = "~/provider_codes.csv",
        stringsAsFactors = FALSE
      ) %>% select(biu_hospital_id, hospital, hospital_group_long_name),
      by = "biu_hospital_id",
      all.x = TRUE
    ) %>% select(hospital_group_long_name, hospital, date, total8am),
    by = "hospital",
    all = TRUE
  ) %>% mutate(
    yv = total8am*100/count
  ) %>% subset(
    !(hospital %in% c("Temple Street", "Tallaght Paed", "Crumlin")) 
  ) -> D

D %>% pull(date) %>% unique() %>% format("%B %Y") -> sbttl

D %>% ggplot() + 
  
  geom_point(aes(x = pet, y = yv, color = hospital_group_long_name), size = txt_sz) + 
  
  geom_text(size = txt_sz, key_glyph = "rect", aes(x = pet, y = yv, color = hospital_group_long_name, label = hospital, family = "Trebuchet MS"), check_overlap = FALSE, vjust = 1.5) +
  
  geom_line(aes(x = pet, y = median(yv)), color = "grey31", size = 5) +
  
  geom_line(aes(x = median(pet), y = yv), color = "grey31", size = 5) +
  
  geom_text(aes(x = median(pet), y = max(yv), label = paste0(" Median: ", round(median(pet), 1)), family = "Trebuchet MS"), hjust = "left", color = "grey31", size = txt_sz) +
  
  geom_text(color = "grey31", aes(x = min(pet), y = median(yv), label = paste0(" Median: ", round(median(yv), 1)), family = "Trebuchet MS"), hjust = "left", vjust = -0.5, size = txt_sz) +
  
  labs(x = "Average PET for ED Departures (Hours)", y = "Trolleys per 100 Departures", title = "Trolley-PET Performance", subtitle = sbttl) + 
  
  scale_x_continuous(limits = c(floor(min(D$pet)), ceiling(max(D$pet))), breaks = seq(from = floor(min(D$pet)), to = ceiling(max(D$pet))))+
  
  scale_y_continuous(limits = c(floor(min(D$yv)), ceiling(max(D$yv))), breaks = seq(from = floor(min(D$yv)), to = ceiling(max(D$yv)), by = 5))+
  
  scale_color_manual(values = c(blue, orange, red, lightblue, green, yellow)) +

  theme(panel.background = x, legend.title = x, text = f1, axis.line = element_line(color = "grey31", size = 5), legend.position = "top", legend.key = x, plot.title = title_style, plot.subtitle = subtitle_style)
```


## Trolleys per 100 Admissions Vs Mean Admitted PET

```{r quadrant2}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(
    destination %in% admDests
    & complete.cases(depart) 
    & departmonth == max(regmonth)
    & complete.cases(age)
    & age >= 16
  ) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>% select(biu_hospital_id, hospital),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    count = sum(count),
    pet = mean(pet)
  ) %>%
  ungroup() %>%
  select(hospital, count, pet) %>%
  distinct() %>% merge(
    y = read.csv(
      file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
      stringsAsFactors = FALSE
    ) %>% select(Hospital.Code, Target.Date, Total.8am) %>% rename(
      biu_hospital_id = Hospital.Code,
      date = Target.Date,
      total8am = Total.8am
    ) %>% mutate(
      date = as.Date(
        format(
          as.Date.character(
            date,
            "%d/%m/%Y"
          ),
          "%Y-%m-01"
        )
      )
    ) %>% subset(
      date == max(date)
    ) %>% group_by(biu_hospital_id) %>% mutate(
      total8am = sum(total8am)
    ) %>% ungroup() %>% select(
      biu_hospital_id, total8am
    ) %>% distinct() %>% merge(
      y = read.csv(
        file = "~/provider_codes.csv",
        stringsAsFactors = FALSE
      ) %>% select(biu_hospital_id, hospital, hospital_group_long_name),
      by = "biu_hospital_id",
      all.x = TRUE
    ) %>% select(hospital_group_long_name, hospital, total8am),
    by = "hospital",
    all = TRUE
  ) %>% mutate(
    yv = total8am*100/count
  ) %>% subset(
    !(hospital %in% c("Temple Street", "Tallaght Paed", "Crumlin")) 
  ) -> D

D %>% ggplot() + 
  
  geom_point(aes(x = pet, y = yv, color = hospital_group_long_name), size = txt_sz) + 
  
  geom_text(size = txt_sz, key_glyph = "rect", aes(x = pet, y = yv, color = hospital_group_long_name, label = hospital, family = "Trebuchet MS"), check_overlap = FALSE, vjust = 1.5) +
  
  geom_line(aes(x = pet, y = median(yv)), color = "grey31", size = 5) +
  
  geom_line(aes(x = median(pet), y = yv), color = "grey31", size = 5) +
  
  geom_text(aes(x = median(pet), y = max(yv), label = paste0(" Median: ", round(median(pet), 1)), family = "Trebuchet MS"), hjust = "left", color = "grey31", size = txt_sz) +
  
  geom_text(color = "grey31", aes(x = min(pet), y = median(yv), label = paste0(" Median: ", round(median(yv), 1)), family = "Trebuchet MS"), hjust = "left", vjust = -0.5, size = txt_sz) +
  
  labs(x = "Average PET for ED Admissions (Hours)", y = "Trolleys per 100 Admissions", title = "Trolleys-PET Performance (Admissions)", subtitle = sbttl) + 
  
  scale_x_continuous(limits = c(floor(min(D$pet)), ceiling(max(D$pet))), breaks = seq(from = floor(min(D$pet)), to = ceiling(max(D$pet))))+
  
  scale_y_continuous(limits = c(floor(min(D$yv)), ceiling(max(D$yv))), breaks = seq(from = floor(min(D$yv)), to = ceiling(max(D$yv)), by = 5))+
  
  scale_color_manual(values = c(blue, orange, red, lightblue, green, yellow)) +

  theme(panel.background = x, legend.title = x, text = f1, axis.line = element_line(color = "grey31", size = 5), legend.position = "top", legend.key = x, plot.title = title_style, plot.subtitle = subtitle_style)
```

# Patient Experience Time

## Median PET By Hospital

```{r medianPETByHosp}
edData %>%
  mutate(
    count = 1,
    regmonth = as.Date(
      format(
        reg, 
        "%Y-%m-01"
      )
    ),
    departmonth = as.Date(
      format(
        depart,
        "%Y-%m-01"
      )
    )
  ) %>%
  subset(
    departmonth == max(regmonth)
    & complete.cases(depart)
  ) %>%
  mutate(
    pet = as.numeric(
      difftime(
        depart,
        reg,
        units = "hours"
      )
    )
  ) %>%
  
  mutate(natmedian = median(pet)) %>%
  
  group_by(biu_hospital_id) %>% mutate(pet = median(pet)) %>% ungroup() %>%
  
  mutate(clr = ifelse(pet == natmedian, "National Median", ifelse(pet < natmedian, "Below National Median", "Above National Median"))) %>%
  
  select(departmonth, biu_hospital_id, pet, natmedian, clr) %>%
  
  distinct() %>%
  
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(biu_hospital_id, hospital) %>%
      subset(complete.cases(biu_hospital_id)),
    by = "biu_hospital_id",
    all.x = TRUE
  ) -> D

D %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl
  
  D %>% ggplot(aes(y = pet, x = reorder(hospital, pet), fill = clr)) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", key_glyph = "rect") +
  
  geom_text(size = txt_sz,
            
            color = "grey31",
            
            key_glyph = "rect", 
            
            aes(label = round(pet, 1), family = "Trebuchet MS"), hjust = "left") +
  
  labs(x = "", y = "Hours", title = "Median PET", subtitle = sbttl) + 
  
  scale_fill_manual(values = c(red, green)) +
  
  guides(fill = guide_legend(override.aes = list(size = 30))) +
  
  theme(panel.background = x, 
        
        plot.title = title_style,
        
        plot.subtitle = subtitle_style,
        
        legend.title = x, 
        
        text = f1, 
        
        axis.line = x,
        
        panel.grid.major.x = grid_line,
        
        legend.position = "top"
        
        )
```

## PET Performance

```{r petPerformance}
edData %>%
  subset(
    complete.cases(depart)
    & as.Date(depart) <= max(as.Date(reg))
  ) %>%
  mutate(
    pet = ifelse(
      depart >= reg,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      ),
      NA
    ),
    petlt6 = ifelse(pet < 6, 1, 0),
    petlt9 = ifelse(pet < 9, 1, 0),
    month = as.Date(format(depart, "%Y-%m-01"))
  ) %>%
  subset(complete.cases(pet)) %>%
  group_by(month) %>%
  mutate(
    petlt6 = mean(petlt6),
    petlt9 = mean(petlt9)
  ) %>%
  ungroup() %>%
  select(month, petlt6, petlt9) %>%
  distinct() %>%
  arrange(month) %>%
  
  melt("month") %>%
  
  mutate(variable = ifelse(variable == "petlt6", "PET < 6 Hours", "PET < 9 Hours")) -> D

D %>% ggplot(aes(x = month, color = variable)) + 
  
  geom_point(aes(y = value), size = pnt_sz, key_glyph = "rect") + geom_line(aes(y = value), size = line_sz, key_glyph = "rect") +
  
  labs(title = "% of ED Departures") + 
  
  scale_x_date(breaks = D$month, labels = format(D$month, "%b %Y")) +
  
  scale_y_continuous(breaks = seq(from = round(min(D$value), 1), to = round(max(D$value), 1), by = 0.05), labels = paste0(round(100*seq(from = round(min(D$value), 1), to = round(max(D$value), 1), by = 0.05)), "%")) +
  
  scale_color_manual(values = c(blue, green)) +
  
  guides(color = guide_legend(override.aes = list(size = 30))) +
  
  geom_text(aes(y = value, label = paste0(round(100*value, 1), "%")), color = "grey31", family = "Trebuchet MS", size = txt_sz, vjust = "top") +
  
  theme(panel.background = x, text = f1, legend.title = x, axis.title = x, legend.key = x, legend.position = "top", axis.text.x = rotated_f1, axis.line.y = element_line(color = "grey31", size = 2), plot.title = title_style, panel.grid.major.y = grid_line)
```

## PET Distribution

```{r petdist}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(complete.cases(depart) & departmonth == max(regmonth)) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    petbin = ifelse(
      floor(pet) == pet,
      pet + 1,
      ceiling(pet)
    ),
    count = 1
  ) %>%
  subset(complete.cases(pet)) %>%
  group_by(petbin) %>%
  mutate(count = sum(count)) %>%
  ungroup() %>%
  distinct(petbin, count, departmonth) %>%
  arrange(petbin) %>%
  mutate(
    running = cumsum(count),
    petrate = running/max(running)
  ) -> D

# subplot(
# 
#   D %>% subset(petbin < 25) %>%
#     plot_ly(x = ~petbin) %>%
#     add_trace(
#       type = "scatter",
#       mode = "lines+markers",
#       y = ~petrate,
#       marker = list(color = red, width = 15),
#       line = list(color = red, width = 10)
#     ) %>%
#     add_annotations(
#       data = D %>% subset(petbin %in% c(3, 6, 9, 12, 15, 18, 21, 24)),
#       showarrow = FALSE,
#       y = ~petrate,
#       xanchor = "left",
#       text = ~paste0(round(100*petrate, 1), "%")
#     ) %>%
#     add_annotations(
#       data = D %>% subset(petbin == 6),
#       y = ~petrate,
#       ax = 600,
#       ay = 450,
#       text = ~paste(
#         "6 Hour PET",
#         paste0("Performance: ", round(100*petrate, 1), "%"),
#         sep = "\n"
#       )
#     ) %>%
#     add_annotations(
#       data = D %>% subset(petbin == 9),
#       y = ~petrate,
#       ax = 1200,
#       ay = 60,
#       text = ~paste(
#         "9 Hour PET",
#         paste0("Performance: ", round(100*petrate, 1), "%"),
#         sep = "\n"
#       )
#     ) %>%
#     layout(
#       yaxis = list(
#         title = "Cumulative Fraction of Total Records",
#         tickformat = "%"
#       )
#     ),
#   
#   D %>%
#     subset(petbin < 25) %>%
#     plot_ly(x = ~petbin, showlegend = FALSE) %>%
#     add_bars(y = ~count, marker = list(color = blue)) %>%
#     add_annotations(
#       showarrow = FALSE,
#       yanchor = ~ifelse(petbin < 10, "top", "bottom"),
#       color = ~ifelse(petbin < 10, "white", "grey31"),
#       y = ~count,
#       textangle = 90,
#       text = ~format(count, big.mark = ",")
#     ) %>%
#     layout(
#       yaxis = list(
#         title = "Number of records"
#       )
#     ),
#   
#   nrows = 2,
#   shareX = TRUE,
#   titleY = TRUE
# ) %>%
#   layout(
#     xaxis = list(
#       title = "PET (bin)",
#       tickvals = c(0, 3, 6, 9, 12, 15, 18, 21, 24)
#     ),
#     margin = list(l = 5, t = 5, b = 5, r = 5),
#     font = list(
#       family = "Trebuchet MS",
#       size = 80,
#       color = "grey31"
#     ))
D %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

D %>% subset(petbin <= 24) %>%
  
  ggplot(aes(x = petbin, y = petrate, label = ifelse(petbin %in% c(1,3,6,9,12,15,18,21,24), paste0(round(100*petrate, 1), "%"), ""))) + 
  
  geom_point(size = pnt_sz, color = red) + 
  
  geom_line(size = line_sz, color = red) + 
  
  geom_text(size = txt_sz, color = "grey31", family = "Trebuchet MS") +
  
  labs(title = "Count of Total ED Departures and % of Cumulative Total", subtitle = sbttl, x = NULL, y = "% of Cumulative Total") + 
  
  scale_y_continuous(labels = scales::percent, breaks = c(0,0.25,0.5,0.75,1)) +
  
  theme(plot.title = title_style, plot.subtitle = subtitle_style, panel.background = x, panel.grid.major.y = grid_line, axis.title.x = x, axis.title.y = f1, axis.line = x, axis.ticks = x, axis.text.y = f1, axis.text.x = x) -> p1

D %>% subset(petbin <= 24) %>% 
  
  ggplot(aes(x = petbin, y = count)) + 
  
  geom_bar(stat = "identity", fill = blue) + 
  
  geom_text(mapping = aes(label = ifelse(count < 0.5*max(count), format(count, big.mark = ","), "")), angle = 90, family = "Trebuchet MS", size = txt_sz, hjust = "left", color = "grey31") + 
  
  geom_text(mapping = aes(label = ifelse(count < 0.5*max(count), "", format(count, big.mark = ","))), angle = 90, family = "Trebuchet MS", size = txt_sz, hjust = "right", color = "white") + 
  
  #scale_y_continuous(limits = c(0, 1.1*max(D$count))) + 
  
  scale_x_continuous(breaks = seq(1,24)) + 
  
  labs(x = "Number of Hours in ED", y = "Count of ED Departures") + 
  
  theme(plot.title = x, plot.subtitle = x, panel.background = x, axis.title = f1, axis.line = x, axis.ticks = x, axis.text = f1, panel.grid.major.y = grid_line) -> p2

ggplotGrob(p1) -> g1; ggplotGrob(p2) -> g2
rbind(g1, g2, size = "first") -> g
grid.newpage()
grid.draw(g)
```


## PET 6 & 9 Hour Performance By Hospital

```{r pet69byhosp}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth)) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1,
    pet6 = ifelse(pet < 6, 1, 0),
    pet9 = ifelse(pet < 9, 1, 0)
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(hospital, biu_hospital_id),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    pet6 = mean(pet6),
    pet9 = mean(pet9)
  ) %>%
  ungroup() %>%
  select(departmonth, hospital, pet6, pet9) %>%
  distinct() -> D

D %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

D %>% ggplot(aes(y = pet6, x = reorder(hospital, pet9), label = paste0(round(100*pet6, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = blue) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = sbttl, y = "PET < 6 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text = f1, axis.title = f1, plot.title = title_style, plot.subtitle = subtitle_style) -> p1

D %>% ggplot(aes(y = pet9, x = reorder(hospital, pet9), label = paste0(round(100*pet9, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = green) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = sbttl, y = "PET < 9 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text.x = f1, axis.text.y = x, axis.title = f1, plot.title = x, plot.subtitle = x) -> p2

ggplotGrob(p1) -> g1
ggplotGrob(p2) -> g2
cbind(g1, g2, size = "first") -> g
grid.newpage()
grid.draw(g)
```

## PET 6 & 9 Hour Performance By Hospital (Admitted)

```{r admpet69byhosp}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth) & destination %in% admDests) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1,
    pet6 = ifelse(pet < 6, 1, 0),
    pet9 = ifelse(pet < 9, 1, 0)
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(hospital, biu_hospital_id),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    pet6 = mean(pet6),
    pet9 = mean(pet9)
  ) %>%
  ungroup() %>%
  select(hospital, pet6, pet9) %>%
  distinct() -> D

D %>% ggplot(aes(y = pet6, x = reorder(hospital, pet9), label = paste0(round(100*pet6, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = blue) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = sbttl, y = "PET < 6 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text = f1, axis.title = f1, plot.title = title_style, plot.subtitle = subtitle_style) -> p1

D %>% ggplot(aes(y = pet9, x = reorder(hospital, pet9), label = paste0(round(100*pet9, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = green) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = paste0("Admissions | ", sbttl), y = "PET < 9 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text.x = f1, axis.text.y = x, axis.title = f1, plot.title = x, plot.subtitle = x) -> p2

ggplotGrob(p1) -> g1
ggplotGrob(p2) -> g2
cbind(g1, g2, size = "first") -> g
grid.newpage()
grid.draw(g)
```

## PET 6 & 9 Hour Performance By Hospital (Not-Admitted)

```{r nadmpet69byhosp}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth) & !(destination %in% admDests)) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1,
    pet6 = ifelse(pet < 6, 1, 0),
    pet9 = ifelse(pet < 9, 1, 0)
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(hospital, biu_hospital_id),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    pet6 = mean(pet6),
    pet9 = mean(pet9)
  ) %>%
  ungroup() %>%
  select(hospital, pet6, pet9) %>%
  distinct() -> D

D %>% ggplot(aes(y = pet6, x = reorder(hospital, pet9), label = paste0(round(100*pet6, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = blue) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = sbttl, y = "PET < 6 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text = f1, axis.title = f1, plot.title = title_style, plot.subtitle = subtitle_style) -> p1

D %>% ggplot(aes(y = pet9, x = reorder(hospital, pet9), label = paste0(round(100*pet9, 1), "%"))) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = green) + 
  
  geom_text(hjust = "right", family = "Trebuchet MS", color = "white", size = txt_sz) +
  
  scale_y_continuous(limits = c(0,1), labels = scales::percent) + 
  
  labs(title = "PET Performance By Hospital", subtitle = paste0("Non-Admissions | ", sbttl), y = "PET < 9 Hours", x = "") +
  
  theme(panel.background = x, panel.grid.major.x = grid_line, axis.line = x, axis.ticks = x, axis.text.x = f1, axis.text.y = x, axis.title = f1, plot.title = x, plot.subtitle = x) -> p2

ggplotGrob(p1) -> g1
ggplotGrob(p2) -> g2
cbind(g1, g2, size = "first") -> g
grid.newpage()
grid.draw(g)
```

## PET >= 24 Hours

```{r pet24tbl}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth)) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1,
    petgt24 = ifelse(pet >= 24, 1, 0),
    pet24 = 1 - petgt24
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(hospital, biu_hospital_id),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    departures = sum(count),
    petgt24count = sum(petgt24),
    pet24prob = mean(pet24)
  ) %>%
  ungroup() %>%
  select(departmonth, hospital, departures, petgt24count, pet24prob) %>%
  distinct() %>%
  arrange(-pet24prob) -> pet24tbl

pet24tbl %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

pet24tbl %>% select(hospital, departures, petgt24count, pet24prob) %>%
  rbind(data.frame(hospital = "<b>Total</b>",
                   departures = sum(pet24tbl$departures),
                   petgt24count = sum(pet24tbl$petgt24count),
                   pet24prob = 1 - sum(pet24tbl$petgt24count)/sum(pet24tbl$departures))) %>% 
  mutate(departures = format(departures, big.mark = ","),
         petgt24count = format(petgt24count, big.mark = ","),
         pet24prob = paste0(round(100*pet24prob, 1), "%"),
         departures = ifelse(hospital == "<b>Total</b>", paste0("<b>", departures, "</b>"), departures),
         petgt24count = ifelse(hospital == "<b>Total</b>", paste0("<b>", petgt24count, "</b>"), petgt24count),
         pet24prob = ifelse(hospital == "<b>Total</b>", paste0("<b>", pet24prob, "</b>"), pet24prob),
         petgt24count = gsub(" ", "", petgt24count),
         departures = gsub(" ", "", departures)) -> D

names(D) = c("<b>Hospital</b>", "<b>Departures</b>", "<b>PET &ge 24 Hours</b>", "<b>PET < 24 Hours</b>")

D %>% plot_ly() %>%
  add_table(
    rownames = FALSE,
    header = list(
      height = 30,
      values = c(paste0("<b>PET Greater Than 24 Hours</b><br><i>", sbttl, "</i><br> <br><b>Hospital</b>"), "<br><br><br><br><b>Departures</b>", "<br><br><br><br><b>PET >= 24 Hours</b>", "<br><br><br><br><b>PET < 24 Hours</b>"),
      fill = list(color = "white"),
      line = list(width = 0),
      align = rep("left", 3)
    ),
    cells = list(
      height = 30,
      align = rep("left", 3),
      line = list(width = 0),
      fill = list(
        color = list(
          rep(
            c(
              rep("white", nrow(D)-1),
              "white"
            ),
            3
          )
        )
      )
    )
  ) %>%
    layout(
      font = list(
        family = "Trebuchet MS",
        size = 22,
        color = "grey31"
      ),
      autosize = FALSE,
      width = 1300,
      height = 1100,
      margin = list(t = 5, b = 5, l = 5, r = 5)
    ) %>%
    export(file = "petgt24tbl.png")
```


## PET >= 24 Hours (Ages 75+)

```{r petgt24over75tbl}
edData %>%
  mutate(
    departmonth = as.Date(format(depart, "%Y-%m-01")),
    regmonth = as.Date(format(reg, "%Y-%m-01"))
  ) %>%
  subset(departmonth == max(regmonth) & complete.cases(age) & age >= 75 & age < 110) %>%
  mutate(
    pet = ifelse(
      depart < reg,
      NA,
      as.numeric(
        difftime(
          depart,
          reg,
          units = "hours"
        )
      )
    ),
    count = 1,
    petgt24 = ifelse(pet >= 24, 1, 0),
    pet24 = 1 - petgt24
  ) %>%
  subset(complete.cases(pet)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>%
      select(hospital, biu_hospital_id),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(
    departures = sum(count),
    petgt24count = sum(petgt24),
    pet24prob = mean(pet24)
  ) %>%
  ungroup() %>%
  select(departmonth, hospital, departures, petgt24count, pet24prob) %>%
  distinct() %>%
  arrange(-pet24prob) -> pet24tbl

pet24tbl %>% pull(departmonth) %>% unique() %>% format("%B %Y") -> sbttl

pet24tbl %>% select(hospital, departures, petgt24count, pet24prob) %>%
  rbind(data.frame(hospital = "<b>Total</b>",
                   departures = sum(pet24tbl$departures),
                   petgt24count = sum(pet24tbl$petgt24count),
                   pet24prob = 1 - sum(pet24tbl$petgt24count)/sum(pet24tbl$departures))) %>% 
  mutate(departures = format(departures, big.mark = ","),
         petgt24count = format(petgt24count, big.mark = ","),
         pet24prob = paste0(round(100*pet24prob, 1), "%"),
         departures = ifelse(hospital == "<b>Total</b>", paste0("<b>", departures, "</b>"), departures),
         petgt24count = ifelse(hospital == "<b>Total</b>", paste0("<b>", petgt24count, "</b>"), petgt24count),
         pet24prob = ifelse(hospital == "<b>Total</b>", paste0("<b>", pet24prob, "</b>"), pet24prob),
         petgt24count = gsub(" ", "", petgt24count),
         departures = gsub(" ", "", departures)) -> D

names(D) = c("<b>Hospital</b>", "<b>Departures</b>", "<b>PET &ge 24 Hours</b>", "<b>PET < 24 Hours</b>")

D %>% plot_ly() %>%
  add_table(
    rownames = FALSE,
    header = list(
      height = 30,
      values = c(paste0("<b>PET Greater Than 24 Hours</b><br><i>Ages 75+ | ", sbttl, "</i><br> <br><b>Hospital</b>"), "<br><br><br><br><b>Departures</b>", "<br><br><br><br><b>PET >= 24 Hours</b>", "<br><br><br><br><b>PET < 24 Hours</b>"),
      fill = list(color = "white"),
      line = list(width = 0),
      align = rep("left", 3)
    ),
    cells = list(
      height = 30,
      align = rep("left", 3),
      line = list(width = 0),
      fill = list(
        color = list(
          rep(
            c(
              rep("white", nrow(D)-1),
              "white"
            ),
            3
          )
        )
      )
    )
  ) %>%
    layout(
      font = list(
        family = "Trebuchet MS",
        size = 22,
        color = "grey31"
      ),
      autosize = FALSE,
      width = 1300,
      height = 1100,
      margin = list(t = 5, b = 5, l = 5, r = 5)
    ) %>%
    export(file = "petgt24over75tbl.png")
```

# Trolleys

## Trolleys Month & YTD

```{r trolleytbl, eval = FALSE}
read.csv(file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
         stringsAsFactors = FALSE) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(biu_hospital_id = Hospital.Code, 
         date = Target.Date, 
         total8am = Total.8am) %>%
  mutate(date = as.Date.character(date, "%d/%m/%Y"),
         year = as.integer(format(date, "%Y")),
         month = as.integer(format(date, "%m")),
         year1 = ifelse(year == max(year), total8am, 0),
         year0 = ifelse(year == max(year) - 1, total8am, 0)) %>%
  subset(year >= max(year) - 1 & !(biu_hospital_id %in% c(940, 941, 992))) %>%
  group_by(biu_hospital_id, month) %>%
  mutate(year1 = sum(year1),
         year0 = sum(year0),
         thisyear = max(year)) %>%
  ungroup() %>%
  select(biu_hospital_id, thisyear, month, year0, year1) %>%
  distinct() %>%
  arrange(biu_hospital_id, month) %>%
  group_by(biu_hospital_id) %>%
  mutate(ytdyear0 = cumsum(year0),
         ytdyear1 = cumsum(year1)) %>%
  ungroup() %>%
  subset(year1 != 0) %>%
  subset(month == max(month)) %>%
  merge(y = read.csv(file = "~/provider_codes.csv",
                     stringsAsFactors = FALSE) %>% select(
                       biu_hospital_id, 
                       hospital_group_long_name,
                       hospital
                      ),
        by = "biu_hospital_id",
        all.x = TRUE) %>%
  arrange(
    hospital_group_long_name, 
    hospital
  ) -> trolleystbl

trolleystbl %>% rbind(data.frame(biu_hospital_id = 9999,
                                 thisyear = max(trolleystbl$thisyear),
                                 month = max(trolleystbl$month),
                                 year0 = sum(trolleystbl$year0),
                                 year1 = sum(trolleystbl$year1),
                                 ytdyear0 = sum(trolleystbl$ytdyear0),
                                 ytdyear1 = sum(trolleystbl$ytdyear1),
                                 hospital_group_long_name = "Total",
                                 hospital = "")) %>%
  mutate(change = ifelse(year0 == 0, NA, (year1 - year0)/year0),
         ytdchange = ifelse(ytdyear0 == 0, NA, (ytdyear1 - ytdyear0)/ytdyear0),
         change = ifelse(
           is.na(change), "",
           ifelse(
             change < 0,
             paste0(round(100*change, 1), "%"),
             paste0("+", round(100*change, 1), "%")
           )
         ),
         ytdchange = ifelse(
           is.na(ytdchange), "",
           ifelse(
             ytdchange < 0,
             paste0(round(100*ytdchange, 1), "%"),
             paste0("+", round(100*ytdchange, 1), "%")
           )
         )
  ) -> trolleystbl

for(c in c("year0", "year1", "ytdyear0", "ytdyear1")){
  trolleystbl[, c] = format(trolleystbl[, c], big.mark = ",")
}

YYYY1 = trolleystbl %>% pull(thisyear) %>% unique()
YYYY0 = YYYY1 - 1

MMMM = paste(
  YYYY1,
  trolleystbl %>% pull(month) %>% unique(),
  1,
  sep = "-"
) %>% 
  as.Date() %>%
  format("%B")

trolleystbl %>%
  mutate(
    gap1 = "", 
    gap2 = "",
    hospital_group_long_name = ifelse(
      duplicated(hospital_group_long_name),
      "",
      hospital_group_long_name
    )
  ) %>%
  select(
    hospital_group_long_name, 
    hospital, 
    year0, 
    year1, 
    gap1, 
    ytdyear0, 
    ytdyear1, 
    gap2, 
    change, 
    ytdchange
  ) %>%
  plot_ly() %>% 
  add_table(
    rownames = FALSE,
    columnwidth = c(4, 2, 1, 1, 1, 1, 1, 1, 1, 1),
    header = list(
      height = 30,
      values = c(
        "", 
        "",
        paste(MMMM, YYYY0, sep = "<br>"),
        paste0(MMMM, "<br>", YYYY0, " YTD"),
        "", 
        paste(MMMM, YYYY1, sep = "<br>"), 
        paste0(MMMM, "<br>", YYYY1, " YTD"), 
        "", 
        "% Change<br>Month", 
        "% Change<br>YTD"
      ),
      align = c("left", "left", rep("center", 8)),
      line = list(width = 0),
      fill = list(
        color = c(
          "skyblue", "skyblue", "skyblue", "skyblue",
          "white", 
          "skyblue", "skyblue", 
          "white",  
          "skyblue", "skyblue"
        )
      )
    ),
    cells = list(
      height = 25,
      align = c("left", "left", rep("center", 8)),
      line = list(width = 0),
      fill = list(
        color = list(
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          "white",
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          "white",
          c(rep("white", nrow(trolleystbl)-1), "skyblue"),
          c(rep("white", nrow(trolleystbl)-1), "skyblue")
        )
      )
    )
  ) %>%
  layout(
    font = list(
      family = "Trebuchet MS",
      size = 16,
      color = "grey31"
    ),
    autosize = FALSE,
    width = 1300,
    height = 975,
    margin = list(t = 5, b = 5, r = 5, l = 5)
  ) %>% export(
    file = "trolleytbl.png"
  )
```


## 30-Day Moving Average (Year on Year Comparison)

```{r trolleys30dmavYvY}
read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(
    biu_hospital_id = Hospital.Code, 
    date = Target.Date,
    total = Total.8am
  ) %>%
  mutate(
    date = as.Date.character(date, "%d/%m/%Y"),
    year = as.integer(format(date, "%Y")),
    monthNumber = as.integer(format(date, "%m")),
    thisyear = max(year)
  ) %>%
  subset(date >= as.Date("2017-12-01")) %>%
  group_by(date) %>%
  mutate(total = sum(total)) %>%
  ungroup() %>%
  select(year, date, total) %>%
  distinct() %>%
  arrange(date) %>%
  mutate(
    mav30 = 0,
    chartDate = as.Date(
      paste(
        max(year), 
        format(date, "%m-%d"),
        sep = "-"
      )
    )
  ) %>%
  data.frame() -> D

for(r in 2:nrow(D)){
  D[r, "mav30"] = subset(
    D,
    date %in% seq.Date(
      from = D[r, "date"] - 30,
      to = D[r, "date"],
      by = "days"
    )
  ) %>% 
    pull(total) %>%
    mean()
}

seq.Date(from = min(D$chartDate), to = max(D$chartDate), by = "month") -> xbreaks
format(xbreaks, "%B") -> xlabels

D %>% 
  
  subset(year >= max(year)-2) %>%
  
  ggplot(aes(x = chartDate, y = mav30, color = factor(year))) +
  
  geom_line(size = line_sz, key_glyph = "rect") +
  
  scale_color_manual(values = c(red, blue, green)) +
  
  scale_x_date(breaks = xbreaks, labels = xlabels) +
  
  labs(title = "30-Day Moving Average of Trolley Count") +
  
  theme(panel.background = x, axis.title = x, legend.title = x, legend.key = x, legend.position = "top", legend.direction = "horizontal", axis.line = element_line(size = 1, color = "grey31"), text=  f1, axis.text.x = rotated_f1, panel.grid.major = grid_line) + legendFixColor
```

## 30-Day Moving Average

```{r trolleys30dmav}
seq.Date(from = min(D$date), to = max(D$date), by = "month") -> xbreaks
format(xbreaks, "%b %Y") -> xlabels

D %>% 
  
  subset(year >= max(year)-2) %>%
  
  ggplot(aes(x = date, y = mav30, color = factor(year))) +
  
  geom_line(size = line_sz, key_glyph = "rect") +
  
  scale_color_manual(values = c(red, blue, green)) +
  
  scale_x_date(breaks = xbreaks, labels = xlabels) +
  
  labs(title = "30-Day Moving Average of Trolley Count") +
  
  theme(panel.background = x, axis.title = x, legend.title = x, legend.key = x, legend.position = "top", legend.direction = "horizontal", axis.line = element_line(size = 1, color = "grey31"), text=  f1, axis.text.x = rotated_f1, panel.grid.major = grid_line) + legendFixColor
```

## Monthly Trolley Count by Hospital

```{r trolleycountbyhosp}
read.csv(
  file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
  stringsAsFactors = FALSE
) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(
    biu_hospital_id = Hospital.Code, 
    date = Target.Date,
    total = Total.8am
  ) %>%
  mutate(
    date = as.Date.character(date, "%d/%m/%Y"),
    year = as.integer(format(date, "%Y")),
    month = as.Date(format(date, "%Y-%m-01")),
    monthNumber = as.integer(format(date, "%m"))
  ) %>%
  subset(month == max(month)) %>%
  merge(
    y = read.csv(
      file = "~/provider_codes.csv",
      stringsAsFactors = FALSE
    ) %>% select(biu_hospital_id, hospital),
    by = "biu_hospital_id",
    all.x = TRUE
  ) %>%
  group_by(hospital) %>%
  mutate(sum = sum(total)) %>%
  ungroup() %>%
  select(month, hospital, sum) %>%
  distinct() -> D

D %>% ggplot(aes(x = reorder(hospital, sum), y = sum)) + geom_bar(stat = "identity", aes(fill = sum)) + coord_flip() + geom_text(aes(label = format(sum, big.mark = ",")), hjust = "left", size = txt_sz, family = "Trebuchet MS", color = "grey31") + theme(axis.title = x, axis.ticks = x, axis.line = x, axis.text = f1, plot.title = title_style, plot.subtitle = subtitle_style, panel.background = x, panel.grid.major.x = grid_line) + guides(fill = "none") + labs(title = "Total Daily Trolley Count", subtitle = D %>% pull(month) %>% unique() %>% format("%B %Y")) + scale_fill_gradient(high = "darkred", low = "pink") + scale_y_continuous(limits = c(0, 1.05*max(D$sum)))
```

## % Contribution to Trolley Count

```{r trolleycontrib}
read.csv(file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
         stringsAsFactors = FALSE) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(biu_hospital_id = Hospital.Code, 
         date = Target.Date, 
         total8am = Total.8am) %>%
  mutate(date = as.Date.character(date, "%d/%m/%Y"),
         year = as.integer(format(date, "%Y")),
         month = as.integer(format(date, "%m")),
         year1 = ifelse(year == max(year), total8am, 0),
         year0 = ifelse(year == max(year) - 1, total8am, 0)) %>%
  subset(year >= max(year) - 1) %>%
  group_by(biu_hospital_id, month) %>%
  mutate(year1 = sum(year1),
         year0 = sum(year0),
         thisyear = max(year)) %>%
  ungroup() %>%
  select(biu_hospital_id, thisyear, month, year0, year1) %>%
  distinct() %>%
  subset(year1 != 0) %>%
  subset(month == max(month)) %>%
  merge(y = read.csv(file = "~/provider_codes.csv",
                     stringsAsFactors = FALSE) %>% select(biu_hospital_id, hospital),
        by = "biu_hospital_id",
        all.x = TRUE) %>%
  select(hospital, thisyear, month, year0, year1) %>%
  mutate(year0contrib = year0/sum(year0),
         year1contrib = year1/sum(year1),
         year0lbl = paste0(round(100*year0contrib, 1), "%"),
         year1lbl = paste0(round(100*year1contrib, 1), "%")) %>%
  arrange(hospital) -> D

YYYY1 = D %>% pull(thisyear) %>% unique()
YYYY0 = YYYY1 - 1

D %>% mutate(t = format(as.Date(paste(thisyear-1, month, 1, sep = "-")), "%B %Y")) %>% pull(t) %>% unique() -> xt0
D %>% mutate(t = format(as.Date(paste(thisyear, month, 1, sep = "-")), "%B %Y")) %>% pull(t) %>% unique() -> xt1

D %>% ggplot(aes(x = reorder(hospital, year1contrib), y = year0contrib, label = year0lbl)) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = green) + 
  
  geom_text(color = "grey31", hjust = "left", size = txt_sz, family = "Trebuchet MS") + 
  
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05*max(D$year0contrib))) + 
  
  theme(axis.ticks = x, axis.title.y = x, panel.background = x, panel.grid.major.x = grid_line, axis.text = f1, axis.title.x = f1) +
  
  labs(y = xt0) -> p1

D %>% ggplot(aes(x = reorder(hospital, year1contrib), y = year1contrib, label = year1lbl)) + 
  
  coord_flip() + 
  
  geom_bar(stat = "identity", fill = blue) + 
  
  geom_text(color = "grey31", hjust = "left", size = txt_sz,  family = "Trebuchet MS") + 
  
  scale_y_continuous(labels = scales::percent, limits = c(0, 1.05*max(D$year1contrib))) + 
  
  theme(axis.text.y = x, axis.text.x = f1, axis.title.y = x, axis.title.x = f1, axis.ticks = x, panel.background = x, panel.grid.major.x = grid_line) + 
  
  labs(y = xt1) -> p2


g1 = ggplotGrob(p1); g2 = ggplotGrob(p2)
cbind(g1, g2, size = "first") -> g
grid.newpage()
grid.draw(g)
# subplot(
# 
#   tbl %>% plot_ly(
#     type = "bar",
#     x = ~year0contrib,
#     y = ~reorder(hospital, year1contrib),
#     marker = list(color = green)
#   ) %>% add_annotations(
#     showarrow = FALSE,
#     xanchor = "left",
#     text = ~paste0(round(100*year0contrib, 1), "%")
#   ) %>%
#     layout(
#       xaxis = list(
#         title = paste("Contribution to", YYYY0, "Total"),
#         tickformat = "%"
#       )
#     ),
#   tbl %>% plot_ly(
#     showlegend = FALSE,
#     type = "bar",
#     x = ~year1contrib,
#     y = ~reorder(hospital, year1contrib),
#     marker = list(color = blue)
#   ) %>% add_annotations(
#     showarrow = FALSE,
#     xanchor = "left",
#     text = ~paste0(round(100*year1contrib, 1), "%")
#   ) %>%
#     layout(
#       xaxis = list(
#         title = paste("Contribution to", YYYY1, "Total"),
#         tickformat = "%"
#       )
#     ),
#   nrows = 1,
#   shareY = TRUE,
#   titleX = TRUE
# ) %>%
#   layout(
#     yaxis = list(
#       title = "",
#       autotick = FALSE
#     ),
#     font = list(
#       family = "Trebuchet MS",
#       size = 80,
#       colour = "grey31"
#     ),
#     yaxis = list(
#     margin = list(t = 5, b = 5, r = 5, l = 5)
#     )
#   )
```

## Change in YTD Trolley Count

```{r changeytdtrolleys, eval=FALSE}
read.csv(file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
         stringsAsFactors = FALSE) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(biu_hospital_id = Hospital.Code, 
         date = Target.Date, 
         total8am = Total.8am) %>%
  mutate(date = as.Date.character(date, "%d/%m/%Y"),
         year = as.integer(format(date, "%Y")),
         month = as.integer(format(date, "%m")),
         year1 = ifelse(year == max(year), total8am, 0),
         year0 = ifelse(year == max(year) - 1, total8am, 0)) %>%
  subset(year >= max(year) - 1) %>%
  group_by(biu_hospital_id, month) %>%
  mutate(year1 = sum(year1),
         year0 = sum(year0),
         thisyear = max(year)) %>%
  ungroup() %>%
  select(biu_hospital_id, thisyear, month, year0, year1) %>%
  distinct() %>%
  arrange(biu_hospital_id, month) %>%
  group_by(biu_hospital_id) %>%
  mutate(ytdyear0 = cumsum(year0),
         ytdyear1 = cumsum(year1)) %>%
  ungroup() %>%
  subset(year1 != 0) %>%
  subset(month == max(month)) %>%
  merge(y = read.csv(file = "~/provider_codes.csv",
                     stringsAsFactors = FALSE) %>% select(biu_hospital_id, hospital),
        by = "biu_hospital_id",
        all.x = TRUE) %>%
  arrange(hospital) %>%
  mutate(ytdchange = ytdyear1 - ytdyear0,
         ytdchangepc = ifelse(ytdyear0 == 0, NA, ytdchange/ytdyear0),
         ytdchangepclabel = ifelse(is.na(ytdchangepc), "",
                                   ifelse(ytdchangepc < 0, 
                                          paste0(round(100*ytdchangepc, 1), "%"), 
                                          paste0("+", round(100*ytdchangepc, 1), "%"))),
         ytdchangelabel = ifelse(ytdchange < 0, 
                                 format(ytdchange, big.mark = ","),
                                 paste0("+", ytdchange)))-> tbl

YYYY1 = tbl %>% pull(thisyear) %>% unique()
YYYY0 = YYYY1 - 1

MMMM = paste(
  YYYY1,
  tbl %>% pull(month) %>% unique(),
  1,
  sep = "-"
) %>% 
  as.Date() %>%
  format("%B")

tbl %>% plot_ly(
  type = "bar",
  x = ~ytdchange,
  y = ~reorder(hospital, ytdchange),
  marker = ~list(color = ifelse(ytdchange < 0, green, red))
) %>% add_annotations(
  showarrow = FALSE,
  text = ~ytdchangelabel,
  xanchor = ~ifelse(ytdchange < 0, "right", "left")
) %>% layout(
  yaxis = list(
    title = "",
    autotick = FALSE
  ),
  xaxis = list(
    title = "Change in YTD Total Trolleys"
  ),
  font = list(
    family = "Trebuchet MS",
    size = 80,
    colour = "grey31"
  ),
  margin = list(t = 5, b = 5, r = 5, l = 5)
)
```

```{r changeytdtrolleys2}
read.csv(file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
         stringsAsFactors = FALSE) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(biu_hospital_id = Hospital.Code, 
         date = Target.Date, 
         total8am = Total.8am) %>%
  mutate(date = as.Date.character(date, "%d/%m/%Y"),
         year = as.integer(format(date, "%Y")),
         month = as.integer(format(date, "%m")),
         year1 = ifelse(year == max(year), total8am, 0),
         year0 = ifelse(year == max(year) - 1, total8am, 0)) %>%
  subset(year >= max(year) - 1) %>%
  group_by(biu_hospital_id, month) %>%
  mutate(year1 = sum(year1),
         year0 = sum(year0),
         thisyear = max(year)) %>%
  ungroup() %>%
  select(biu_hospital_id, thisyear, month, year0, year1) %>%
  distinct() %>%
  arrange(biu_hospital_id, month) %>%
  group_by(biu_hospital_id) %>%
  mutate(ytdyear0 = cumsum(year0),
         ytdyear1 = cumsum(year1)) %>%
  ungroup() %>%
  subset(year1 != 0) %>%
  subset(month == max(month)) %>%
  merge(y = read.csv(file = "~/provider_codes.csv",
                     stringsAsFactors = FALSE) %>% select(biu_hospital_id, hospital),
        by = "biu_hospital_id",
        all.x = TRUE) %>%
  arrange(hospital) %>%
  mutate(ytdchange = ytdyear1 - ytdyear0,
         ytdchangepc = ifelse(ytdyear0 == 0, NA, ytdchange/ytdyear0),
         ytdchangepclabel = ifelse(is.na(ytdchangepc), "",
                                   ifelse(ytdchangepc < 0, 
                                          paste0(round(100*ytdchangepc, 1), "%"), 
                                          paste0("+", round(100*ytdchangepc, 1), "%"))),
         ytdchangelabel = ifelse(ytdchange < 0, 
                                 format(ytdchange, big.mark = ","),
                                 paste0("+", ytdchange)),
         increase = ifelse(ytdchange > 0, "A", "B"))-> D

YYYY1 = D %>% pull(thisyear) %>% unique() %>% as.integer()
YYYY0 = YYYY1 - 1

MMMM = paste(
  YYYY1,
  D %>% pull(month) %>% unique(),
  1,
  sep = "-"
) %>% 
  as.Date() %>%
  format("%B")

D %>% ggplot(aes(x = reorder(hospital, ytdchange), y = ytdchange, label = ytdchangelabel, fill = increase)) + geom_bar(stat = "identity") + coord_flip() + geom_text(color = "grey31", hjust = ifelse(D$ytdchange >= 0, "left", "right"), family = "Trebuchet MS", size = txt_sz) + scale_fill_manual(values = c(red, green)) + guides(fill = "none") + labs(title = "Change in YTD Trolley Count", subtitle = YYYY1) + theme(panel.background = x, axis.title = x, axis.ticks = x, plot.title = title_style, plot.subtitle = subtitle_style, axis.text = f1, panel.grid.major.x = grid_line)
```

## % Change in YTD Trolley Count

```{r pcchangeytdtrolleys, eval=FALSE}
read.csv(file = "C:/Users/jack.lyons/Downloads/TrolleyGAR.csv",
         stringsAsFactors = FALSE) %>%
  select(Hospital.Code, Target.Date, Total.8am) %>%
  rename(biu_hospital_id = Hospital.Code, 
         date = Target.Date, 
         total8am = Total.8am) %>%
  mutate(date = as.Date.character(date, "%d/%m/%Y"),
         year = as.integer(format(date, "%Y")),
         month = as.integer(format(date, "%m")),
         year1 = ifelse(year == max(year), total8am, 0),
         year0 = ifelse(year == max(year) - 1, total8am, 0)) %>%
  subset(year >= max(year) - 1) %>%
  group_by(biu_hospital_id, month) %>%
  mutate(year1 = sum(year1),
         year0 = sum(year0),
         thisyear = max(year)) %>%
  ungroup() %>%
  select(biu_hospital_id, thisyear, month, year0, year1) %>%
  distinct() %>%
  arrange(biu_hospital_id, month) %>%
  group_by(biu_hospital_id) %>%
  mutate(ytdyear0 = cumsum(year0),
         ytdyear1 = cumsum(year1)) %>%
  ungroup() %>%
  subset(year1 != 0) %>%
  subset(month == max(month)) %>%
  merge(y = read.csv(file = "~/provider_codes.csv",
                     stringsAsFactors = FALSE) %>% select(biu_hospital_id, hospital),
        by = "biu_hospital_id",
        all.x = TRUE) %>%
  arrange(hospital) %>%
  mutate(ytdchange = ytdyear1 - ytdyear0,
         ytdchangepc = ifelse(ytdyear0 == 0, NA, ytdchange/ytdyear0),
         ytdchangepclabel = ifelse(is.na(ytdchangepc), "",
                                   ifelse(ytdchangepc < 0, 
                                          paste0(round(100*ytdchangepc, 1), "%"), 
                                          paste0("+", round(100*ytdchangepc, 1), "%"))),
         ytdchangelabel = ifelse(ytdchange < 0, 
                                 format(ytdchange, big.mark = ","),
                                 paste0("+", ytdchange)))-> tbl

YYYY1 = tbl %>% pull(thisyear) %>% unique()
YYYY0 = YYYY1 - 1

MMMM = paste(
  YYYY1,
  tbl %>% pull(month) %>% unique(),
  1,
  sep = "-"
) %>% 
  as.Date() %>%
  format("%B")

tbl %>% plot_ly(
  type = "bar",
  x = ~ytdchangepc,
  y = ~reorder(hospital, ytdchangepc),
  marker = ~list(color = ifelse(ytdchange < 0, green, red))
) %>% add_annotations(
  showarrow = FALSE,
  text = ~ytdchangepclabel,
  xanchor = ~ifelse(ytdchange < 0, "right", "left")
) %>% layout(
  yaxis = list(
    title = "",
    autotick = FALSE
  ),
  xaxis = list(
    title = "% Change in YTD Total Trolleys",
    tickformat = "%"
  ),
  font = list(
    family = "Trebuchet MS",
    size = 80,
    colour = "grey31"
  ),
  margin = list(t = 5, b = 5, r = 5, l = 5)
)
```

```{r pcchangeytdtrolleys2}
D %>% ggplot(aes(x = reorder(hospital, ytdchangepc), y = ytdchangepc, label = ytdchangepclabel, fill = increase)) + geom_bar(stat = "identity") + coord_flip() + geom_text(color = "grey31", size = txt_sz, family = "Trebuchet MS", hjust = ifelse(D$ytdchangepc >= 0, "left", "right")) + scale_fill_manual(values = c(red, green)) + guides(fill = "none") + labs(title = "% Change in YTD Trolley Count", subtitle = YYYY1) + theme(panel.background = x, axis.title = x, axis.ticks = x, plot.title = title_style, plot.subtitle = subtitle_style, axis.text = f1, panel.grid.major.x = grid_line)
```

```{r cleanup}
rm(list = ls())
```