---
# title: "National Acute Hospital Review: Inpatients and Outpatients"
output: 
  flexdashboard::flex_dashboard:
    # orientation: rows
    vertical_layout: fill
    number_sections: true
---

```{r setup, include=FALSE}
rm(list=ls())

library(flexdashboard)

fls=list.files(
  
  path='~/Markdown/ed_kpi_dashboard/r_scripts/',
  
  pattern='.R',
  
  full.names=T
  
  )

for(i in fls){source(i)}

rm(i,fls)
# trolleygar_df=create_trolleygar_df()
# ed_df=create_ed_df()

load("~/Markdown/ed_kpi_dashboard/ed_and_trolleygar.RData")

hse_group=0

```

Executive Summary
=================

### Executive Summary
```{r}
ed_exec_summary(hse_group)
```


ED Attendances
=======================================

Row {.tabset}
--------------

### Bar Chart Trend
```{r}
ed_attends_bar_chart(hse_group)
```

### Line Trend
```{r}
ed_attends_line_chart(hse_group)
```


### Age Profile Trend
```{r}
ed_attends_age_trend(hse_group)
```

### Age Profile Trend (% of Total)
```{r}
ed_attends_age_percent_trend(hse_group)
```

### Age Profile (Pie)
```{r}
ed_attends_age_pie_chart(hse_group)
```

### Age-Group Detail
```{r}
ed_attends_age_bar_chart()
```

ED Tables
=========================================

Column {.tabset}
----------------

### ED Attendances
```{r}
ed_attends_tables(hse_group,1)
```

### ED Attendances (Ages 0-15)
```{r}
ed_attends_tables(hse_group,2)
```

### ED Attendances (Ages 75+)
```{r}
ed_attends_tables(hse_group,3)
```


Column {.tabset}
-----------------------------------------------------------------------

### ED Admissions
```{r}
ed_admissions_tables(hse_group,1)
```

### ED Admissions (Ages 0-15)
```{r}
ed_admissions_tables(hse_group,2)
```

### ED Admissions (Ages 75+)
```{r}
ed_admissions_tables(hse_group,3)
```


ED Departures
=============

Row {.tabset}
-------------

### Admissions & Non-Admissions by Hospital
```{r}
adm_rate_bar_chart(hse_group)
```

### Admission Rates By Hospital (Table)
```{r}
adm_rate_table()
```

### Registrations By Hour
```{r}
ed_attends_by_hour(hse_group)
```

### Admissions By Hour
```{r}
ed_admissions_by_hour(hse_group)
```

### Discharge Destination (Pie)
```{r}
ed_departures_destination_pie_chart(hse_group)
```

### Discharge Destination (Table)
```{r}
ed_departures_destination_table(hse_group,1)
```

Quadrant
========

Row {.tabset}
----------------

### Mean PET & 8 am Trolley Count per 100 Departures
```{r}
quadrant_chart_1(hse_group)
```

### Mean PET (Admitted) & 8 am Trolley Count per 100 Admissions
```{r}
quadrant_chart_2(hse_group)
```

PET
=====

Row {.tabset}
--------------

### Mean PET By Hospital
```{r}
mean_pet_by_hospital_bar_chart(hse_group)
```

### PET Performance Trend
```{r}
pet_performance_trend_line(hse_group)
```

### PET Distribution
```{r}
pet_distribution(hse_group)
```

### PET Performance By Hospital
```{r}
pet_performance_by_hospital(hse_group)
```

### PET Performance By Selected Patient Cohorts
```{r}
pet_performance_by_cohort(hse_group)
```

### PET > 24 Hours
```{r}
pet_gt_24_tbl(hse_group)
```

### PET > 24 Hours (75+)
```{r}
pet_over75_gt_24_tbl(hse_group)
```

Trolleys
========

Row {.tabset}
--------------

### 8am Trolley Count (Table)
```{r}
trolleygar_table(hse_group)
```

### 30 Day Moving Average (Year on Year Comparison)
```{r}
nat_trolleygar_30dma_yvy()
```

### 30 Day Moving Average (Continuous)
```{r}
nat_trolleygar_30dma_cont()
```

### Monthly Trolley Count By Hospital
```{r}
trolleygar_count_by_hospital(hse_group)
```

### Change in YTD Trolley Count
```{r}
trolleygar_difference_by_hospital(hse_group,0)
```

### Change in YTD Trolley Count (%)
```{r}
trolleygar_difference_by_hospital(hse_group,1)
```
